### 2020-11-14 template/paper/paper.tex
FirstCommit

%
% paper.tex  
%    システム制御情報学会論文誌  論文・研究速報用Ａ４版クラスファイル
%    scitrans.cls のサンプル（論文のテンプレートファイル）
%
\documentclass[J]{scitrans}
\usepackage{graphicx}
%
%               Usage:  \documentclass[J]{scitrans} (和文の場合)
%                       \documentclass[E]{scitrans} (英文の場合)

%
% 年, 巻, 号 ページの設定
%

%
\appearyear{0000}                           %% 投稿時は変更しないでください
\vol{0}                                     %% 投稿時は変更しないでください
\numberinvol{0}                             %% 投稿時は変更しないでください
\setcounter{page}{1}
\setcounter{volumepage}{1}

\Transaction                                    %% 論文および研究速報のとき
%%\Shortpaper                                   %% 研究速報のとき

\ForSubmission                                %% 論文投稿時には
                                                %% コメントをはずしてください

\begin{document}

\title{システム制御情報学会スタイルファイルの\\ 使い方 論文誌用}
\author{鈴木　太郎${}^\dagger$・佐藤　花子$^\ddagger$・田中　次郎${}^\dagger$}
\etitle{Usage of the Style File for Transactions of the Institute of
        Systems, Control and Information Engineers}
\eauthor{Taro {\sc Suzuki}${}^\dagger$, Hanako {\sc Sato}${}^\ddagger$
 and Jiro {\sc Tanaka}${}^\dagger$}
\headingtitle{システム制御情報学会スタイルファイルの使い方}
\headingauthors{鈴木・佐藤・田中}

%% 論文要旨(論文および研究速報のときに書いてください)
%
\ronbunyoushi{
      論文要旨
      論文の要旨はこうである．論文の要旨はこうである．
      論文の要旨はこうである．論文の要旨はこうである．
      論文の要旨はこうである．論文の要旨はこうである．
      論文の要旨はこうである．論文の要旨はこうである．
      論文の要旨はこうである．論文の要旨はこうである．
      論文の要旨はこうである．論文の要旨はこうである．}

%% 英文要旨(論文のときのみ書いてください)
%
\abstract{
        This is an abstract.  This is an abstract.
        This is an abstract.  This is an abstract.
        This is an abstract.  This is an abstract.
        This is an abstract.  This is an abstract.
        This is an abstract.  This is an abstract.
        This is an abstract.  This is an abstract.
        This is an abstract.  This is an abstract.}

\maketitle

\acceptdate{1995年8月1日}

\address{*}{\AcceptDate}

%%%「講演論文等をもとにした投稿論文の取り扱い方針」に従い，システム制御情報学会研究発表講演会など本学会が主催する講演会やシンポジウムでの速報性の高い講演論文を元にして論文を投稿する場合は，以下にその旨を記入して下さい．論文の所定の脚注部に記載されます．
\address{*}{第○○回システム制御情報学会研究発表講演会にて発表(20××年△△月)}

\address{**}{〇〇大学　大学院　工学研究科　Graduate School of Engineering, OO University;
        Yoshida-Honmachi, Sakyo ward, Kyoto city, Kyoto 606-01, JAPAN}
\address{***}{××大学　基礎工学部　Faculty of Engineering Science,
        XX University;
        1-3 Machikaneyamacho, Toyonaka city, Osaka 560, JAPAN}
\keywords{style file, transactions, ISCIE, paper.}

%%% つぎの \input を削除し，本文を書き出して下さい．
\input{tmp.tex}

\end{document}
%
%% end of paper.tex

### 2020-11-14 template/paper/paper_e.tex
FirstCommit

% paper_e.tex  
%    A manuscript sample for submission to Transactions of the Institute of 
%    Systems, Control and Information Engineers

%Authors: Please do not make any changes on the commands below.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[E]{scitrans}
%\usepackage{graphicx}
\usepackage{math}
\usepackage{bm}
\usepackage[dvipdfmx]{graphicx,xcolor}
\usepackage[dvipdfmx]{epsfig}
%
\appearyear{0000}
\vol{0}
\numberinvol{0}
\setcounter{page}{1}
\setcounter{volumepage}{1}
\Transaction
%%\Shortpaper
\ForSubmission
%Authors: Please do not make any changes on the commands above.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%Authors: If you wish to use packages, please include them here.
%%         Note that only "amsfonts" and "psfrag" packages are available.
%%         The "latexsym" package has been already included.
%\usepackage{amsfonts}
%\usepackage{psfrag}

%Authors: Please follow the format below to fill in: paper's title, authors' 
%         names and affiliations, paper's condensed title and authors' names,
%         abstract and keywords.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\title{DESIGN OF A TWO-PIECE BRASSIERE CUP TO FIT BREAST DATA POINTS TOWARD ITS AUTOMATION}

\author{Kotaro {\sc Yoshida}${}^\dagger$, Hidefumi {\sc Wakamatsu}${}^\dagger$, Eiji {\sc Morinaga}${}^\ddagger$, and Takahiro {\sc Kubo}${}^\S$}

%Authors: Please write paper's short title and authors' names.
\headingtitle{DESIGN BRASSIERE CUP TO FIT BREAST DATA POINTS}
\headingauthors{{\sc Yoshida}, {\sc Wakamatsu}, {\sc Morinaga} and {\sc Kubo}}

%Authors: Please copy the abstract of your paper.
\abstract{
       A method to design the two-dimensional shapes of patterns of two piece brassiere cup is proposed when its target three-dimensional shape is given as a cloud of its data points. A brassiere cup consists of several patterns and their shapes are designed by repeatedly making a paper cup model and checking its three-dimensional shape. For improvement of design efficiency of brassieres, such trial and error must be reduced. As a cup model for check is made of paper not cloth, it is assumed that the surface of the model is composed of several developable surfaces. When two lines lying on a developable surface are given, the shape of the surface can be determined. Then, the two-piece brassiere cup can be designed by minimizing the error between the surface and given data points. It was mathematically verified that the original developable surface can be reproduced from data points on it by use of our proposed method.
}

%Authors: Please do not make any changes on the commands below.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\maketitle
\acceptdate{August 1, 1995}
\address{*}{\AcceptDate}
%Authors: Please do not make any changes on the commands above.

%%% In accordance with the ISCIE policy on overlapping conference/journal submissions, if the material of this paper originates from conference papers published in the proceedings of conferences or symposia organized by the ISCIE as preliminary report, the following line should be written at the footnote in the first page of this paper.
\address{*}{The material of this paper was partially presented at the International Symposium on Flexible Automation 2020 which was held in July, 2020.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%Authors: Please write down authors' affiliations and addresses.
\address{**}{Graduate School of Engineering,
	Osaka University;
	Yamadaoka, Suita city, Osaka 565-0871, JAPAN}
\address{***}{Graduate School of Humanities and Sustainable System Sciences,Osaka Prefecture University, 1-1, Gakuencho, Naka-ku, Sakai, Osaka 599-8531, Japan}
\address{****}{Wacoal Holdings Corporation;
	Nakajima-cho, Kisshoin, Minami-ku,Kyoto 601-8530, JAPAN}

%Authors: Please write down the keywords of your paper.
\keywords{design, simulation, theory of surfaces, automation}

%Authors: Please remove \input and write down the body of your paper.
%\input{tmp_e.tex}

\section*{INTRODUCTION}

Developable surfaces that can be unfolded into a plane without expanding and contracting are widely used from shipbuilding to manufacturing of clothing, which are suitable to representation of surfaces that can be made of leather, paper, and sheet metal. In such fields, it is very important to design the two-dimensional shapes of plates which can form the required three-dimensional shape by being bent and joined. In this paper, we focus on production of brassieres, which is related to design of two-dimensional shapes of plates. 
Brassieres are manufactured to meet various demands, such as to enhance a woman's breast size, to create cleavage, or to minimize breast movement. For this reason, the cup shape of a brassiere is very important when designing a brassiere. A brassiere cup is formed by several pieces of cloth called patterns and a wire. For example, as shown in \rfig{fig:patterns}, a two-piece brassiere cup is composed of the upper pattern, the lower pattern and the lower line.
\begin{figure}[h!]
	\centering
	\subfigure[upper pattern]{
		\includegraphics[width=0.45\columnwidth]{./figure/UpperPattern.eps}
		\label{fig:pattern_U}
	}
	\hfil
	\subfigure[lower pattern]{
		\includegraphics[width=0.45\columnwidth]{./figure/LowerPattern.eps}
		\label{fig:pattern_L}
	}
	\\
	\subfigure[lower line]{
		\includegraphics[width=0.35\columnwidth]{./figure/LowerWire.eps}
		\label{fig:Wire}
	}
	\caption{Parts of a two-piece brassiere cup}
	\label{fig:patterns}
\end{figure}
 And the cup has three curves and they are also very important to design. As shown in \rfig{fig:TwoCurves}, one is the wire line corresponding to the boundary between a breast and a body. Another is the ridge line of the cup corresponding to the outline of a bust on a transverse plane. The other is the upper line to connect a cup and shoulder strap.

%==============================================================%
In apparel industries, the form of a product is fixed by fashion designers and pattern makers. Fashion designers draw an image of the product and pattern makers determine the shapes of patterns to meet various demands of the ideal shape, which previously mentioned about a brassiere, and so on.
%%fig
\begin{figure}[h!]
	\centering
	\includegraphics[scale=0.25]{./figure/Lines.eps}
	\caption{Expression of a wire line, a ridge line and an upper line}
	\label{fig:TwoCurves}
\end{figure}
The design process of a brassiere cup is shown in \rfig{fig:process}. In design cite, pattern makers first consider the functional requirement of a brassiere cup based on a breast shape, then determine the pattern shape. Since this design procedure cannot mainly be performed by CAD system but based on experience and intuition, they must check the shapes with a paper model of the cup and modify them repeatedly to realize the function. So, the situation may cause unnecessary repetition of modifying and checking pattern shapes. In order to improve the design efficiency of brassieres, it is required to reduce such trial and error as much as possible. So, in this paper, we focus on the process srrounded by a dotted line in \rfig{fig:process} and aim to automate it. 
When it comes to the function of a brassiere cup, Higuchi researched what emphasis is placed on in design of a brassiere cup\cite{c1}. According to  \cite{c1}, the function: fitting breast is most important. Therefore, we propose a method to design the shapes of patterns of a brassiere cup fitting the given breast shape. The given three-dimensional breast shape is assumed to be given as a cloud of data points, which can be obtained easily by measurement.

\begin{figure}[h!]
	\centering
	\includegraphics[width= 1.0 \columnwidth]{./figure/DesignProcess2.eps}
	\caption{Design process of a brassiere cup}
	\label{fig:process}
\end{figure}

%==============================================================%

As a cup shape is made by bending and sewing each pattern and assumed to be inextensible, the cup model consists of several developble surfaces.
With respect to modeling of develoable surfaces, a method to model developable surface by focusing on the geodesic line\cite{c2}, B-spline or NURBS surface\cite{c3,c4}, offsets of Bartrand curves which coincide each normal direction\cite{c5,c6}, and arbitrary curves on it\cite{c7}. Especially, Martin proposed a method to reconstruct developable surface from its point clouds based on Laguerre geometry\cite{c8}. Also, Chen et al. proposed an algorithm to approximate developable surface from its point cloud\cite{c9}. However, all of them does not reference its developed shape and only focus on a single developable surface. When it comes to manufacturing a brassiere cup, the pattern shapes, i.e. developed shapes of a cup is required, not 3D cup shape. Especially in a study on brassieres, Wakamatsu et al. proposed a method to predict the three-dimensional shape of a paper cup model when the two-dimensional shape of pattern is given \cite{c10,c11}. As a result, evaluation of the patterns becomes possible without actually creating a paper model. However, repetitive modification of the patterns is still required to obtain the target three-dimensional shape of the cup.
Ito et al. developed a paper model CAD system based on the theory of developable surfaces\cite{c12}. If a three-dimensional curve that means a sewn curve and a two-dimensional curve that means a piece to be sewn are given, a feasible region where the sewn surface does not intersect itself can be shown with this system. However, it is difficult to design the shape of patterns, that is, the shape of two-dimensional curves with this system.
We previously proposed method to design pattern shape and its developable surface from two lines: a wire line and a ridge line. They are obtained by solving optimization problem whose design parameters are the geodesic curvatures of a pattern shape and objective function is the error between generatrices determined by the geodesic curvature of a lower edge and the wire line and generatrices determined by the geodesic curvature of an upper edge and the ridge line. However, when it apply to this problem, it is required to  solve this optimization problem until the intended shape\cite{MyRef}. It leads to taking unnecessary time.
%==============================================================%

The products are mainly composed of two or three pieces of pattern. In this paper, we focus on two-piece brassiere cup and aim to propose a method to design its pattern shapes toward improvement of its design efficiency when a cloud of its data points is given.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{MODELING OF DEVELOPABLE SURFACE AND PATTERN SHAPE}

In this section, we aim to explain numerical expression of a developable surface. 
When it comes to a curvature of a space curve on a surface, it is divided to the normal curvature by deforming the surface and the geodesic curvature by deforming a space curve. The geodesic curvature does not change by deforming the surfce as long as it is not stretched. In case of a brassiere cup, the normal curvature can be manipulated by deforming the surface, but the geodesic curvature cannot. So, it is required to design the geodesic curvature in order to coincide a space curve with a boundary of the developable surface. Let \textit{lower edge} be the curve connecting to a lower wire as shown Fig.\ref{fig:pattern_L}, and \textit{upper edge} be the curve combining with upper cup as shown Fig.\ref{fig:pattern_L}. In this section, we aim to propose a method to determine a developable surface by two curves that lie on it and to design the pattern shape from them. We explain the method to express the developable surface from parameters of a space curve , the condition of two lines that lie on the developable surface, and a pattern shape obtained from them.
For this aim, we set object coordinate system on the lower edge of the cup surface as shown \rfig{fig:obj_coord} so that $\zeta$ -axis always coincides the tangential direction of the edge line and $\eta$ -axis always coincides the normal direction of the surface. The posture of the object coordinate system is changed by deformation of the cup. Then, the infinitesimal displacement vector of each axial direction can be described by the infinitesimal rotational ratio vector $ \mbold{\omega} = \left[\omega_{\xi}\;\;\omega_{\eta}\;\;\omega_{\zeta}\right]^{\mathrm{T}}$as follows:

\begin{equation}\label{eq:ObjSys}
\left[\begin{array}{ccc} \xivec' & \etavec' & \zetavec' \end{array}\right] = \left[\begin{array}{ccc} \xivec & \etavec & \zetavec \end{array} \right] \mbold{\Omega}(\mbold{\omega}), 
\end{equation}
where a prime means a derivative of $s$, and $\mbold{\Omega}(\mbold{\omega})$ is represented as follows: 
\begin{equation}
\mbold{\Omega}(\mbold{\omega}) = \left[\begin{array}{ccc}
0 &-\omega_{\zeta} & \omega_{\eta} \\
\omega_{\zeta} & 0 &-\omega_{\xi} \\
-\omega_{\eta} & \omega_{\xi} &0
\end{array}\right]. 
\end{equation}

Then, the tangent vector is expressed as follows: 
\begin{equation}
\zetavec(s) = \zetavec_0 + \int_{0}^{s} \left( \omega_{\eta} \xivec - \omega_{\xi} \etavec \right) ds,
\label{eq:zetav_eq}
\end{equation}
where $\zetavec_0$ represents the tangent vector at $s=0$ and by integrating \req{eq:zetav_eq}, the position of the curve can be calculated as follows:
\begin{equation}
\mbold{x}(s) = \mbold{x}_0 + \int_0^s \zetavec ds, 
\end{equation}
where $\mbold{x}_0$ means the position at $s=0$.

\begin{figure}[thpb]
	\centering
	\includegraphics[width = 0.8\columnwidth]{./figure/Object_Coordinates.eps}
	\caption{Object coordinate system on the surface}
	\label{fig:obj_coord}
\end{figure}

First, we explain numerical expression of developable surface by the constraint of Gaussian curvature. 
In general, a normal curvature of a direction vector $\mbold{d}_{\theta} = \zetavec \cos \theta + \xivec \sin \theta $ can be described using coefficients of the first and the second fundamental forms $E, F, G, L, M$ and $N$:
\begin{equation}\label{eq:def_kappa_theta}
\kappa_{\theta} = \frac{L \cos^2 \theta + 2M \sin \theta \cos \theta + N \sin^2 \theta}{E \cos^2 \theta + 2F \sin \theta \cos \theta + G \sin^2 \theta}.
\end{equation}
And the Gaussian curvature $K$ and the mean curvature $H$, which characterize a surface, can be defined as extreme values of \req{eq:def_kappa_theta}: $ \kappa_{\max} $ and $ \kappa_{\min} $ as follows

\begin{eqnarray}
K &=& \kappa_{\max}  \kappa_{\min}  = \disfrac{LN-M^2}{EG-F^2}, \nonumber \\ 
H &=& \disfrac{\kappa_{\max} + \kappa_{\min}}{2} = \frac{EN-2FM+GL}{2(EG-F^2)}. 
\end{eqnarray}

In this paper, coefficients of first fundamental form are represented as following equation:
\begin{equation}
E = \zetavec \cdot \zetavec = 1, F = \zetavec \cdot \xivec = 0, G = \xivec \cdot \xivec = 1.
\end{equation}
Also, coefficients of second fundamental form are represented as following equation:
\begin{equation}
L = \zetavec' \cdot \eta = -\omega_{\xi}, M = \xivec' \cdot \eta = -\omega_{\zeta}.
\end{equation}
Then, Gaussian curvature $K$ and the mean curvature $H$ are described by
the following equation:

\begin{eqnarray}
\label{eq:GC_expressed_omega}
K &=& -\omega_{\xi} N - \omega_{\zeta}^2, \\
H &=& \disfrac{-\omega_{\xi}+N}{2}.
\end{eqnarray}
Developable surface is defined as the surface whose Gaussian curvature $K = 0$, which means $\kappa_{\min}=0$. Then, the mean curvature can be calculated as $2H=\kappa_{\max}$. This means that a line direction of which coincides with direction $\mbold{d}_{\min}$ is kept straight after deformation. This straight line is referred to as a generatrix. 
In this paper, principal directions are described by using the angle $ \alpha $: 
\begin{eqnarray}\label{eq:d1d2_eq}
\mbold{d}_{\max} &=& \zetavec \cos \alpha + \xivec \sin \alpha, \nonumber \\ 
\mbold{d}_{\min} &=& -\zetavec \sin \alpha + \xivec \cos \alpha.
\end{eqnarray}
The angle $ \alpha $ is referred to as the \textit{rib angle} in this paper.
By solving $ \kappa_{\theta} = 0 $,　the rib angle $ \alpha $ can be calculated as following equation:
\begin{equation}\label{eq:alpha_eq}
\tan \alpha = -\frac{\omega_{\zeta}}{\omega_{\xi}}.
\end{equation}
And from \req{eq:GC_expressed_omega}, $\kappa_1$ is calculated as follows: 
\begin{equation}\label{eq:kappa1_eq}
\kappa_1 = -\frac{\omega_{\xi}^2 + \omega_{\zeta}^2}{\omega_{\xi}}.
\end{equation}
From above, a developable surface can be determined by $\mbold{\omega}$.
%%%%%%%%%%%%%%ここまで7/21

Next, we explain the constraint of developable surface when two curves that lie on the surface are given. Let $s_a$ and $s_b$ be the arc length and $\mbold{x}_a(s_a)$, $\mbold{x}_b(s_b)$ be positions of each curve. We assume that these curves have ${\rm C}^2$ community at least. In general developable surfaces are a special kind of ruled surfaces. When the surface is a ruled surface, a generatrix $ \mbold{g} $ is described as follows:

\begin{equation}
\mbold{g} = \mbold{x}_b(s_b)-\mbold{x}_a(s_a).
\end{equation}

Note that $s_a$ can take an arbitrary value against $ s_b $. Therefore, the variation of a generatrix $ \Delta \mbold{g} $ is described by total differential form as follows:
\begin{equation}
\Delta \mbold{g} = -\zetavec_a \Delta s_a + \zetavec_b \Delta s_b,
\end{equation}
where $ \zetavec_a$ and $\zetavec_b $ are tangent vectors of $ \mbold{x}_a $ and $ \mbold{x}_b $, respectively. Next, let $ \Theta $ be the infinitesimal plane surrounded by four vectors $ \zetavec_a \Delta s_a, \zetavec_b \Delta s_b,\mbold{g}$, and $\mbold{g}+\Delta \mbold{g} $ as shown in \rfig{fig:Theta}. When the ruled surface is a developable surface, the plane $ \Theta $ is a tangent plane without twisting. Therefore, it leads to following equation:
\begin{equation}
\det (\zetavec_a, \mbold{g}, \mbold{g}+\Delta \mbold{g})=0
\end{equation}
By solving it, the following equation is obtained:
\begin{equation}
\det (\zetavec_a, \zetavec_b, \mbold{g})=0
\label{eq:Cond1}
\end{equation}
\begin{figure}[!h]
	\centering
	\includegraphics[width = 0.8\columnwidth]{./figure/Theta.eps}
	\caption{Definition of $ \Theta $}
	\label{fig:Theta}
\end{figure}
It indicates that the arc length of each curve is subordination. When two curves are corresponded to edge lines and $s_b$ can be expressed as $s_b(s_a)$, $\mbold{d}_{\min}\equiv\frac{\mbold{g}}{|\mbold{g}|}$ is established. Then, a rib angle is calculated by \req{eq:d1d2_eq} as follows:
\begin{equation}
\alpha = -\sin^{-1}\left( \mbold{d}_{\min} \cdot \zetavec_a \right).
\end{equation}
Using $\mbold{d}_{\min}$ and $\alpha$, $\mbold{\omega}$ can be represented as following equation:
\begin{equation}\label{eq:omegaVec}
\mbold{\omega} = \left[\begin{array}{c} -\det(\zetavec_a',\zetavec_a, \mbold{d}_{\min} ) \\ \zetavec_a' \cdot \mbold{d}_{\min} \\ \det(\zetavec_a',\zetavec_a, \mbold{d}_{\min} ) \tan \alpha \end{array}\right] 
\end{equation}
Therefore, when two curves that lie on the surface are given, a developable surface can be determined.

Next, we explain how to determine the pattern shape from the developable surface. The planar curve generated by developing the space curve $ \mbold{x}_a $ is defined a the lower curve and that by developing the space $ \mbold{x}_b $ is defined as the upper curve.

We set developed planar coordinate system $ vw $ so that $ v $-axis always coincides the line AB as shown in \rfig{fig:PatternImage}. Let $ \mu_a $ be the angle between the tangential direction of the lower edge and the $ v $-axis. $ \mu_a $ is obtained as follows when the curvature of the lower curve $ \omega_{\eta_a} $  is given:
\begin{equation}\label{eq:mu_eq}
\mu_a = \mu_0 + \int_{0}^{s_a} \omega_{\eta_a} ds_a,
\end{equation}
where $ \mu_0 $ represents the angle of the lower edge at $ s=0 $ and is described later. From \req{eq:mu_eq}, the planar position $ \mbold{x}_{ae} $ is described as follows:
\begin{equation}\label{eq:x_LE}
\mbold{x}_{ae}  = \int_{0}^{s_a} \left[\begin{array}{cc} \cos \mu_a \\ \sin \mu_a \end{array}\right] ds_a
\end{equation}
With respect to \req{eq:mu_eq}, let $ a,b $ be defined as follows:
\begin{eqnarray}
a &=& \int_{0}^{L_a} \cos \left( \int_{0}^{s_a} \omega_{\eta_a} ds\right) ds_a, \\
b &=& \int_{0}^{L_a} \sin \left( \int_{0}^{s_a} \omega_{\eta_a} ds\right) ds_a. 
\end{eqnarray}
Then, $ \mu_0 $ can be calculated as follows:
\begin{equation}\label{eq:mu_0eq}
\mu_0 = \tan^{-1}\frac{b}{a}
\end{equation}
Let $ \mbold{x}_{be} $ be the planar position of an upper edge. Since the rib angle of a pattern $ \alpha_a $ and the length of a generatrix of a pattern $ |\mbold{g}| $ don't change by being developed, $ \mbold{x}_{be} $ can be calculated as follows:
\begin{equation}\label{eq:x_UE}
\mbold{x}_{be} = \mbold{x}_{ae} + |\mbold{g}| \left[\begin{array}{cc} \cos \left(\mu_a + \pi/2 + \alpha_a \right) \\ \sin \left(\mu_a + \pi/2 + \alpha_a \right)  \end{array}\right] 
\end{equation}
From above, a developed shape can be obtained when two curves that lie on the developable surface are given.
\begin{figure}[thpb]
	\centering
	\includegraphics[width = \columnwidth]{./figure/PatternImage2.eps}
	\caption{Description of pattern shape using geodesic curvature of the lower curve}
	\label{fig:PatternImage}
\end{figure}
\section*{EXPRESSION OF DESIGN PROCESS AS OPTIMIZATION PROBLEM}
From section2, the cup shape can be determined by three curves: a wire wire, a ridge line and an upper line. Therefore, when a wire line is given, the objective of our study can be achieved by designing parameters of a ridge line and an upper line, which minimize the degree of fitting to the 3D breast shape. So, in this section, we aim to formulate this degree. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Formulation of the error between a point and a surface}
In order to formulate the degree of fitting to the 3D ideal shape, we formulate the error between a point and a surface.
In general, the position $\mbold{X}(s,t)$ of developable surface $S$ is expressed as following equation:
\begin{equation}\label{eq:Sur_eq}
\mbold{X}(s,t) = \mbold{x}(s) + t\mbold{d}_{\min}(s)
\end{equation}
The distance $\varepsilon(\mbold{p})$ between a point $\mbold{p}$ and a developable surface is formulated by the difference vector $\mbold{\delta}=\mbold{p}-\mbold{X}(s,t)$ as follows:

\begin{equation}\label{eq:eps_eq}
\varepsilon(\mbold{p})=\min_{s,t}{|\mbold{\delta}|}
\end{equation}

When a set of surface parameters $ (s^*,t^*) $ satisfies to minimize \req{eq:eps_eq}, $\mbold{\delta}$ is parallel to $ \etavec $. Therefore, the following equations are satisfied:
\begin{equation}\label{eq:d_mindoteq}
\mbold{d}_{\min} \cdot (\mbold{p} - \mbold{X}(s^*,t^*)) = 0
\end{equation}

\begin{equation}\label{eq:d_maxdoteq}
\mbold{d}_{\max} \cdot (\mbold{p} - \mbold{X}(s^*,t^*)) = 0
\end{equation}
By solving \req{eq:d_mindoteq}, $ t^* $ is described as follows:

\begin{equation}\label{eq:t*_eq}
t^* = \mbold{d}_{\min} \cdot (\mbold{p}-\mbold{X}(s^*))
\end{equation}
By using \req{eq:t*_eq} and solving \req{eq:d_maxdoteq}, $ s^* $ is determined.

Let $ s_w,s_r,s_u $ be arc lengths of a lower wire, ridge line, and upper line and $ \mbold{\omega}_W (s_w ),\mbold{\omega}_R (s_r ),\mbold{\omega}_U (s_u ) $ be vectors to characterize each of them. From \req{eq:Cond1}, $ s_r,s_u $ can be expressed as functions of $ s_w $: $ s_r (s_w ),s_u (s_w ) $. As mentioned, a two-piece brassiere cup is composed of two developable surfaces $ S_L $ and $ S_U $. Let $ D $ be the set of coordinates of points on a breast, $ D_L = \{\mbold{p}_{L,i} \in D \} $ be the set of points to evaluate the surface $ S_L $, and $ D_U = \{\mbold{p}_{U,i} \in D \} $ be the set of points to evaluated the surface $ S_U $, respectively. Note that $ D_U = D \backslash D_L $. Whether a point $ \mbold{p}_k $ is classified to the set of $ D_U $ or the set of $ D_L $ can determined with the length of the nearest generatrix.

First, \req{eq:d_mindoteq,eq:d_maxdoteq,eq:t*_eq}, the nearest surface parameters $ (s_w^*, t_w^*) $ of the lower cup to the point $ \mbold{p}_k $ can be derived. Then, the nearest point $ \mbold{X}(s^*, t^*) $ on the lower cup surface to the point $ \mbold{p}_k $ can be derived. Let $ t_{\max}=|\mbold{x}_R (s_r (s_w^* ))-\mbold{x}_W (s_w^* )| $ be the length of a generatrix on the wire line. If $ t_{\max} > t_w^*(s_w^*) $, that is, if the perpendicular projection point of the point $ \mbold{p}_k $ to the surface $ S_L $ is included in the lower cup, the point $ \mbold{p}_k $ is classified to the set $ D_L $. Otherwise, it is classified to the set $ D_U $. 
\begin{figure}[thpb]
	\centering
	\subfigure[$ t^*\leq t_{\max} $]{
		\includegraphics[width=0.45\columnwidth]{./figure/NotExceeding.eps}
		\label{fig:inD_L}
	}
	\hfil
	\subfigure[$ t^* > t_{\max} $]{
		\includegraphics[width=0.45\columnwidth]{./figure/Exceeding.eps}
		\label{fig:inD_U}
	}
	\caption{Relationship between $ t^*$ and $t_{\max}$.}
	\label{fig:which_in}
\end{figure}

Thus, we can classify point data on a breast into two sets once two developable surfaces for the lower and the upper cup are determined.

From above, the error between the surface of a two-piece brassiere cup and its data points can be formulated:
\begin{equation}\label{eq:Lambda_eq}
\Lambda(D) = \sum_{i=1}^{N_L} \varepsilon(\mbold{p}_{L,i}) + \sum_{i=1}^{N_U} \varepsilon(\mbold{p}_{U,i}).
\end{equation}
By finding two developable surfaces minimizing the error described by \req{eq:Lambda_eq}, appropriate pattern shapes can be determined.

\subsection*{Formulation of Objective Function and Conditions}
Let us consider the conditions of this optimization. First, we explain the conditions about parameters of the ridge line and the upper line. When it comes to designing the space curve, $ \omega_{\zeta} $ does not affect its shape. Therefore, the following conditions are added:
\begin{eqnarray}\label{eq:conds_omgZt}
\omega_{\zeta_R}(s_r(s_w)) &=& 0 \;\; \forall s_w\in[0,L_L], \\
\omega_{\zeta_U}(s_u(s_w)) &=& 0 \;\; \forall s_w\in[0,L_L]. 
\end{eqnarray}

When it comes to designing their arc length, the following  conditions  must be satisfied:
\begin{equation}\label{eq:conds_arc1}
	s_r(s_w) \geq 0 \;\; \forall s_w\in[0,L_L], 
\end{equation}
\begin{equation}\label{eq:conds_arc2}
	s_u(s_w) \geq 0 \;\; \forall s_w\in[0,L_L], 
\end{equation}
\begin{equation}\label{eq:conds_arc3}
	s_r'(s_w) \geq 0 \;\; \forall s_w\in[0,L_L], 
\end{equation}
\begin{equation}\label{eq:conds_arc4}
	s_u'(s_w) \geq 0 \;\; \forall s_w\in[0,L_L].
\end{equation}
In general, the end positions of the ridge line and the upper line are aligned to the end point of the wire line. Therefore, the following equations must be satisfied:
\begin{equation}\label{eq:conds_endp1}
	\mbold{x}_R (s_r(s_w)) = \mbold{x}_L(s_w), 
\end{equation}
\begin{equation}\label{eq:conds_endp2}
	\mbold{x}_U (s_u(s_w)) = \mbold{x}_L(s_w).
\end{equation}

In order to guarantee $ S_L $ and $ S_U $  are developable surfaces, the following equations must be satisfied:
\begin{equation}\label{eq:conds_DevSur1}
	\int_{0}^{L_L} \det (\zetavec_R(s_r(s_w)), \zetavec_W(s_w), \mbold{g}) ds_w = 0,
\end{equation}
\begin{equation}\label{eq:conds_DevSur2}
	\int_{0}^{L_L} \det (\zetavec_U(s_u(s_w)), \zetavec_W(s_w), \mbold{g}) ds_w = 0.
\end{equation}
Next, let us consider a “fuzzy” condition of a brassiere cup. 
The upper line has a point to be connected with a shoulder strap. In this paper, we call this point \textit{connection point}. In design process, this point is usually not given as a unique condition, but a fuzzy condition.
\begin{figure}[!h]
	\centering
	\includegraphics[width = 0.7\columnwidth]{./figure/Connection_Point.eps}
	\caption{Expression about the connection point of a brassiere cup}
	\label{fig:aboutCP}
\end{figure}
It may cause unexpected error of the optimization problem. Therefore, we propose the following equation to deal with this fuzzy condition $ y \simeq Y $:
\begin{equation}\label{eq:FuzzyEq}
C(y,Y) = k_1 \exp( k_2(y-Y)^2 )
\end{equation}
where $ k_1 $ and $ k_2 $ are the variables to adjust a range of satisfying this condition. By adding this equation to the objective function, the fuzzy condition can be dealt. In this paper, we assumed that the position $ \mbold{X}_C $ to connect the upper line and the shoulder strap is given. Then, the objective function $ V $ is described as follows:
\begin{equation}\label{eq:ObjectFunc}
V = \Lambda(\mbold{D}) + \sum_{i=0}^{2} C(\mbold{x}_U \cdot \mbold{e}_i , \mbold{X}_C \cdot \mbold{e}_i)
\end{equation}
where $\mbold{e}_0 $ ,$\mbold{e}_1 $ and $\mbold{e}_2 $ are represented as unit vectors of $ x $,$ y $ and $ z $-axis. By solving this optimization under the constraints, the shape of the brassiere cup, satisfying to fit data points of a breast, can be obtained.

\subsection*{A Procedure of Solving Optimization Problem}
Let us explain a procedure of solving this optimization problem. First, we explain how to eliminate the condition. In order to satisfy \req{eq:conds_arc1,eq:conds_arc2,eq:conds_arc3,eq:conds_arc4}, $ s_r (s_w),s_u (s_w) $ are described using arbitrary functions $ \upsilon_r(s_w),\upsilon_u(s_w) $ as follows:
\begin{eqnarray}
s_r(s_w) &=& s_{r_0} + \int_{0}^{s_w} \upsilon_r^2 ds_w, \\
s_u(s_w) &=& s_{u_0} + \int_{0}^{s_w} \upsilon_u^2 ds_w. 
\end{eqnarray}
When we assume that the initial position of the wire line, that of the ridge line, and that of the upper line are aligned, $ s_{r_0}=s_{u_0}=0 $. Let a composite function of $ s_r(s_w) $ and arbitrary function $ g(s_r) $ be defined as $ \tilde{g}(s_w) $, and a composite function of $ s_u (s_w ) $ and arbitrary function $ g(s_w) $ be defined as $ \hat{g}(s_w) $. Then, from \req{eq:ObjSys}, the object coordinate system of the ridge line and upper line can be expressed as follows:
\begin{equation}\label{eq:tildeobj}
\left[\begin{array}{ccc} \tilde{\xivec}_R' & \tilde{\etavec}_R' & \tilde{\zetavec}_R' \end{array}\right] = s_r' \left[\begin{array}{ccc} \tilde{\xivec}_R & \tilde{\etavec}_R & \tilde{\zetavec}_R \end{array} \right] \Omega(\tilde{\mbold{\omega}}_R)
\end{equation}

\begin{equation}\label{eq:hatobj}
\left[\begin{array}{ccc} \hat{\xivec}_U' & \hat{\etavec}_U' & \hat{\zetavec}_U' \end{array}\right] = s_u' \left[\begin{array}{ccc} \hat{\xivec}_U & \hat{\etavec}_U & \hat{\zetavec}_U \end{array} \right] \Omega(\hat{\mbold{\omega}}_U)
\end{equation}
and the position $ \mbold{x}_R(s_r) \equiv \tilde{\mbold{x}}_R(s_w) $ and $ \mbold{x}_U(s_u) \equiv \hat{\mbold{x}}_U(s_w) $ are expressed by the following equations:
\begin{eqnarray}
\tilde{\mbold{x}}_R(s_w) &=& \int_{0}^{s_w} \tilde{\zetavec}_R s_r' ds_w \\
\hat{\mbold{x}}_U(s_w) &=& \int_{0}^{s_w} \hat{\zetavec}_U s_u' ds_w
\end{eqnarray}

Let $ \mbold{\psi} = [\omega_{\xi} \;\; \omega_{\eta} \;\; \upsilon] $ be the function vector of a line. Then, the vector of the ridge line $ \mbold{\psi}_R $ and the vector of the upper line $ \mbold{\psi}_U $ are represented using Ritz method\cite{c13} as follows:
\begin{equation}\label{eq:R_eq}
\mbold{\psi}_R = \left[ \begin{array}{ccc} \mbold{a}_{\omega_{\xi_R}}& \mbold{a}_{\omega_{\eta_R}}& \mbold{a}_{\upsilon_R} \end{array} \right] \cdot \mbold{e}(s_w) = \mbold{a}_R \cdot \mbold{e}(s_w) 
\end{equation}

\begin{equation}\label{eq:U_eq}
\mbold{\psi}_U = \left[ \begin{array}{ccc} \mbold{a}_{\omega_{\xi_U}}& \mbold{a}_{\omega_{\eta_U}}& \mbold{a}_{\upsilon_U} \end{array} \right] \cdot  \mbold{e}(s_w) = \mbold{a}_U \cdot \mbold{e}(s_w)
\end{equation}
where $ \mbold{e}_i(s) $ is composed of trigonometric functions with different periods. And let $ \mbold{\Phi}_0 = [\xivec_0^\mathrm{T} \;\; \etavec_0^\mathrm{T} \;\; \zetavec_0^\mathrm{T}] $ be an initial basis of the objective coordinate system.

From above, the objective function expressed as \req{eq:ObjectFunc} and geometric constraints expressed as \req{eq:conds_endp1,eq:conds_endp2,eq:conds_DevSur1,eq:conds_DevSur2} are described by the following total parameter vector: 
\begin{equation}\label{eq:TotalCoefs}
\mbold{a}_{\mathrm{all}} = \left[ \begin{array}{cccc}
\mbold{a}_R & \mbold{a}_U & \mbold{\Phi}_{R0} &\mbold{\Phi}_{U0} 
\end{array}\right].
\end{equation}

Consequently, this problem can be converted to a non-linear programming problem. It is solved by the multiplier method and Nelder-Mead method in this paper. By solving the above problem, we can design the entire shape of a two-piece brassiere cup.

\section*{SIMULATION AND VERIFICATION}
In this section, we aim to consider the simulation result and verification of our proposed method. For this verification, the inﬁnitesimal rotational ratios vector $ \mbold{\omega}_W $ of the wire line was given as follows:
\begin{equation}\label{eq:vrf_omgW}
\mbold{\omega}_W = \left[ \begin{array}{ccc}
0 & 2.91 & 0
\end{array}\right]^\mathrm{T}, 
\end{equation}
and, the connection point $ \mbold{X}_C $ was given as follows: 
\begin{equation}\label{eq:givenXc}
\mbold{X}_C = \left[ \begin{array}{ccc}
0 & 0.34 & 0.34
\end{array}\right]^\mathrm{T}.
\end{equation}
We prepared two examples of the simulation.

Case (1): a point cloud on the sphere whose radius is set on R by uniform random number.

Case (2): a point cloud on the set of developable surface by uniform random number using \req{eq:Sur_eq}.

And we aim to confirm two matters by them.
\begin{enumerate}
	\item to design the two-piece brassiere cup which can approximate undevelopable surface, which means it menifests the function: fitting to a breast".
	\item to recreate the same shape that of given shape.
\end{enumerate}
In this study, uniform random number was generated by numpy.random() of Pyhton. At first, we show the result in case(1).

As shown in \rfig{fig:ObtainedSurfaceNDS}, the solid line represents the given wire line, each dotted line does calculated generatrices of the cup shape, and each dots does the given data points. And the pattern shapes were calculated as shown in \rfig{fig:ObtainedSurfaceNDS_Pat}. In \rfig{fig:ObtainedSurfaceNDS_Pat}, each solid line represents a lower edge and a dotted line represents an upper edge. In this result, we could confirm that the designed cup shape by our proposed method menifests the function:"fitting to a breast".
Next, we show the result in case(2). In \rfig{fig:ObtainedSurfaceDS}, the solid line, each dotted line and dot represent as same as case(1). And the pattern shapes were calculated as shown in \rfig{fig:ObtainedSurfaceDS_Pat}. In \rfig{fig:ObtainedSurfaceDS_Pat}, a solid line and a dotted line represent as same as case(1).

As the calculated shapes approximate the given points, we conclude our proposed method in this paper is useful for efficient design of paper patterns of a two-piece brassiere cup.
\begin{figure}[h]
	\centering
	\subfigure[zx-view]{
		\includegraphics[width=0.6\columnwidth,clip]{./figure/NDS/ObtainedRidgeLinefromz-x.eps}
		\label{fig:zx-NDS}
	}
	\hfil
	\subfigure[zy-view]{
		\includegraphics[width=0.6\columnwidth]{./figure/NDS/ObtainedRidgeLinefromz-y.eps}
		\label{fig:zy-NDS}
	}
	\hfil
	\subfigure[xy-view]{
		\includegraphics[width=0.6\columnwidth]{./figure/NDS/ObtainedRidgeLinefromx-y.eps}
		\label{fig:xy-NDS}
	}
	\caption{Obtained shape and input data points in Case(1)}
	\label{fig:ObtainedSurfaceNDS}
\end{figure}

\begin{figure}[h!]
	\centering
	\subfigure[LOWER PATTERN]{
		\includegraphics[width=0.6\columnwidth]{./figure/NDS/ObtainedPatternL.eps}
		\label{fig:low-NDS}
	}
	\hfil
	\subfigure[UPPER PATTERN]{
		\includegraphics[width=0.6\columnwidth]{./figure/NDS/ObtainedPatternU.eps}
		\label{fig:upp-NDS}
	}

	\caption{Obtained patterns in Case(1)}
	\label{fig:ObtainedSurfaceNDS_Pat}
\end{figure}

\begin{figure}[h]
	\centering
	\subfigure[zx-view]{
		\includegraphics[width=0.6\columnwidth]{./figure/DS/ObtainedRidgeLinefromz-x.eps}
		\label{fig:zx-DS}
	}
	\hfil
	\subfigure[zy-view]{
		\includegraphics[width=0.6\columnwidth]{./figure/DS/ObtainedRidgeLinefromz-y.eps}
		\label{fig:zy-DS}
	}
	\hfil
	\subfigure[zy-view]{
		\includegraphics[width=0.6\columnwidth]{./figure/DS/ObtainedRidgeLinefromx-y.eps}
		\label{fig:xy-DS}
	}
	\caption{Obtained shape and input data points in Case(2)}
	\label{fig:ObtainedSurfaceDS}
\end{figure}

\begin{figure}[h!]
	\centering
	\subfigure[LOWER PATTERN]{
		\includegraphics[width=0.6\columnwidth]{./figure/DS/ObtainedPatternL.eps}
		\label{fig:low-DS}
	}
	\hfil
	\subfigure[UPPER PATTERN]{
		\includegraphics[width=0.6\columnwidth]{./figure/DS/ObtainedPatternU.eps}
		\label{fig:upp-DS}
	}

	\caption{Obtained patterns in Case(2)}
	\label{fig:ObtainedSurfaceDS_Pat}
\end{figure}
\section*{CONCLUSION}
In this paper, we proposed a method to design the cup shape of two-piece brassiere cup and its patterns satisfying the function: "fitting to a breast shape", in case that it is given as a cloud of data points. We claimed the background and problem of design process of a brassiere cup. In design process, as a cup model for check of the shapes of patterns is made of paper, it is assumed that the surface of the model is composed of several developable surfaces. At first, we formulated the cup model based on the differential geometry. And we claimed that a developable surface can be determined by two curves included in it. The design process of a two-piece brassiere cup can be converted to the optimization problem, whose objective function is the error between the cup shape and its data points. In order to calculate the error, we first formulated the error between a point and the surface from geometry condition. Then, we proposed a method to divide a data cloud into two clouds: evaluating the lower cup, or evaluating the upper cup. In order to verification of our proposed method, we prepared two examples of data points: a set of non-developable surface and developable surface. From the result of two examples, we confirmed that our proposed method can design the cup shape which manifests the function. As a result, Our proposed method will be useful for efficient design of a two-piece brassiere cup.

%a this paper, a method to design the cup shape of two-piece brassiere cup and its patterns was proposed when its target shape is given as a cloud of data points. As a cup model for check of the shapes of patterns is made of paper, it is assumed that the surface of the model is composed of several developable surfaces. We claimed that a developable surface can be determined by two curves included in it. The design process of a two-piece brassiere cup can be converted to the optimization problem, whose objective function is the error between the cup shape and its data points. In order to calculate the error, we proposed a method to divide a data cloud into two clouds: evaluated by the lower cup, or evaluated by the upper cup. It was experimentally verified that the cup shape calculated by our proposed method reproduced the given data points well. Our proposed method will be useful for efficient design of not only patterns of a brassiere cup but also plate parts of a structure consisting of developable surfaces.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\bibliography{asme2ebackup}

\begin{thebibliography}{99}

	\bibitem{c1}Yukiko Higuchi, {\it Sensory test of brassiere}, in The Japanese Journal of Ergonomics, Volume 20, Issue 2, 1984, pp.73-80, (Japanese).
	\bibitem{c2} P.Bo and W.Wang, {\it "Geodesic-Controlled Developable Surfaces for Modeling Paper Bending"}, in Computer Graphics Forum, Volume 26, 2007, pp.365-374.
	\bibitem{c3} H.Pottmann and J.Wallner, {\it "Approximation algorithms for developable surfaces"}, in Computer Aided Geometric Design, Volume 16, 1999, pp.539-556.
	\bibitem{c4} K.Rose, A.Sheffer, J.Wither, M.Cani, and B.Thibert, {\it "Developable surfaces from arbitrary sketched boundaries"}, SGP ’07 Proceedings of the ﬁfth Eurographics symposium on Geometry processing, 2007, pp.163-172.
	\bibitem{c5} G.Aumann, {\it "A simple algorithm for designing developable Bezier surfaces"}, in Computer Aided Geometrix Design Volume 20, 2003, pp.601-619.
	\bibitem{c6} B.Ravani and T.S. Ku, {\it "Bertrand offsets of ruled and developable surfaces"} in Computer-Aided Design Volume 23, 1991, pp.145-152. 
	\bibitem{c7}R.M.C Bodduluri and B.Ravani, {\it "Design of developable surfaces using duality between plane and point geometries"}, in Computer Aided Design Volume 25, 1993, pp.621-632.
	\bibitem{c8}M. Peternell, {\it "Developable surface fitting to point clouds"}, in Computer Aided Design Vol.21, 2004, pp.785-803.
	\bibitem{c9}H.-Y. Chen, I.-K. Lee, S. Leopoldseder, H. Pottmann, T. Randrup , J. Wallner, {\it "On Surface Approximation using Developable Surfaces"}, Graphical Models and Image Processing, Volume 61, Issue2, 1999, pp.110-124
	\bibitem{c10} H.Wakamatsu, Y.Ryu, E.Morinaga, E.Arai, and T. Kubo, M.Oyama, and T.Kishimoto, {\it "3D Shape Prediction of A Paper Model of Two Piece Brassiere Cup for Its Efficient Design"}, Proc.Int. Symp. Flexible Automation, 2016, pp.326-332
	\bibitem{c11} H.Wakamatsu, E.Morinaga, E.Arai, and T. Kubo, {\it "A Virtual Paper Model of a Three Piece Brassiere Cup to Improve the Efficiency of Cup Design Process"}, Proc. 2017 IEEE Int. Conf. on Robotics and Automation, 2017. 
	\bibitem{c12}M.Itoh, and H.Imaoka, {\it "A Method of Prediction Sewn Shapes and a Possibility of Sewing by the Theory of Developable Surfaces"}, J. the Japan Research Association for Textile End-Uses, Volume 48, 2007, pp.42-51, (Japanese).
	\bibitem{MyRef} Kotaro Yoshida, Hidefumi Wakamatsu, Eiji Morinaga, Eiji Arai, Seiichiro Tsutsumi, Takahiro Kubo,{\it "Pattern Shape Optimization of a Two-piece brassiere cup to improve its design efficiency"}, Trans. of the Institute of Systems, Control and Information Engineers, Volume 32, No. 5, 2019, pp. 192-202.
	\bibitem{c13}Elsgolc L.E {\it Calculus of Variations}, Pergamon Press, 1961, pp. 144-157.
\end{thebibliography}

\authorbiography{Kotaro, YOSHIDA}{}{Non-Member}{%
	Kotaro Yoshida received his B.Eng. and M.Eng. degree from Osaka University in 2017 and 2019, respectively. He is doing a doctoral degree at Osaka University.
}

\authorbiography{Hidefumi, ,WAKAMATSU}{}{Member}{%
	HidefumiWakamatsu received his B.Eng.,
	M.Eng. and Ph.D. degrees from Osaka
	University, Japan, in 1993, 1994 and
	2001, respectively. From 1995 to 2006,
	he worked as a Research Associate, Osaka
	University. He then became an Associate
	Professor at Division of Materials and Manufacturing
	Science, Osaka University. His research interests
	include handling of flexible object. He is a member of
	RSJ, JSME, JSPE, JWS and TMSJ.
}

\authorbiography{Eiji, ,MORINAGA}{}{Member}{%
	Eiji Morinaga received his B.Eng., M.Eng.
	and Ph.D. degrees in Mechanical Engineering
	from Osaka University, Japan,
	in 2000, 2002 and 2005, respectively. From
	2005 to 2007, he worked as a Designated
	Researcher at Center for Advanced Science
	and Innovation, Osaka University. He then became
	an Assistant Professor at Division of Materials and Manufacturing
	Science, Osaka University. His research interests
	include system design and integration in product design
	and manufacturing. He is a member of JSME, JSPE,
	JWS, JIEP and TMSJ.
}

\authorbiography{Takahiro, ,KUBO}{}{Non-Member}{%
	Takahiro Kubo received his B.A. degree in Sport Sciences from Waseda University, Japan, in 2007, and M.A. degree in Arts and Sciences from Tokyo University, Japan, in 2010. He then joined Wacoal Corp. His position is in Human Science Research Center.
}

\end{document}
%
%% end of paper.tex

### 2020-11-14 template/paper/tmp_e.tex
FirstCommit

\section{Introduction}
This document describes how to use the \LaTeX2e class file, named 
``{\tt scitrans.cls}'', for Transactions of the Institute of Systems, 
Control and Information Engineers (ISCIE).

{\tt scitrans.cls} works together with the following nine files: 
\begin{itemize}
\item {\tt scitrans.cls}
\item {\tt sci209.sty, scij.sty, scie.sty, scims.sty}
\item {\tt JT1scimc.fd, JT1scigt.fd}
\item {\tt JY1scimc.fd, JY1scigt.fd}
\end{itemize}
Please make sure that all these files are placed in the same directory 
as the source file and should not be modified.

\section{Sections, etc.}
This is an example of \verb+\section{ }+.

\subsection{Subsections}
This is an example of \verb+\subsection{ }+.

\subsubsection{Sub-Subsections}
This is an example of \verb+\subsubsection{ }+.

\paragraph{Paragraphs}
This is an example of \verb+\paragraph{ }+.
Please insert a blank line before \verb+\paragraph{ }+.

\subparagraph{Subparagraphs}
This is an example of \verb+\subparagraph{ }+.
Please insert a blank line before \verb+\subparagraph{ }+.

\section{Theorems, etc.}
In the {\tt scitrans.cls} class file,
theorems and related structures such as definition, lemma, proposition,
corollary, example, assumption, remark and proof are handled. 
For example,

\begin{theorem}
\label{theorem:1}
This is an example of the theorem environment.
The usage of the lemma, definition, proposition, corollary,
example and assumption environments 
are the same as that of the theorem environment.
\end{theorem}

\begin{proof}
This is an example of the proof environment. 
At the end of each proof, asterisks ``**'' are automatically placed
as the Q.E.D.\ symbol,
whereas they will be replaced by the symbol ``$\Box$'' in the final manuscript.
\end{proof}

\begin{remark}
\label{remark:1}
This is an example of the remark environment. 
\end{remark}

If the author wishes to declare a new theorem-like environment, 
\verb+newtheoremenv+ and \verb+newparenenv+ can be used.
For example,

\begin{newtheoremenv}{Question}
This is an example of declaring a new environment by \verb+newtheoremenv+.
\end{newtheoremenv}
\begin{newparenenv}{Answer}
This is an example of declaring a new environment by \verb+newparenenv+.
\end{newparenenv}

\section{Equations}
Equations are created by the traditional {\tt equation} environment. 
In order to produce multiline equations,
the {\tt eqnarray} environment can be used.
For example,

\begin{eqnarray}
        \dot{\mbf{x}}(t) & = & A \mbf{x}(t) + B \mbf{u}(t) 
                               + \sum_{k=1}^N \Gamma_k \mbf{d}k(t)
                \label{eq:1}\\
        \mbf{y}(t) & = & C \mbf{x}(t) + D \mbf{u}(t)
                \label{eq:2}\\
        \mbf{u}(t) & = & F \mbf{x}(t)
                \label{eq:3}
\end{eqnarray}

\begin{subequations}  \label{eq:4}  
  \begin{eqnarray}
    \lefteqn{ 
        \frac{1}{2\pi} \int_{-\infty}^\infty 
        {\rm Tr}\, \{ \mbf{G}\T(-j\omega) \mbf{G}(j\omega) \} \, d\omega 
     }    \hspace*{2\zw} \nonumber \\
    & = & 
    \frac{1}{2\pi} \int_{-\infty}^\infty 
    {\rm Tr}\, \{  B\T (-j\omega I -A\T)^{-1}C\T \nonumber \\
    &   & 
    \times C (j\omega I - A)^{-1}B \}\, d\omega 
               \label{eq:4a} \\
    & = & 
    \frac{1}{2\pi j}\int_{-j\infty}^{j\infty} 
    {\rm Tr}\, \left\{ 
    \left[ \begin{array}{c|c} 
       A & B \\ \hline 
       C & 0 \end{array} \right]^\sim  
    \left[ \begin{array}{c|c} 
       A & B \\ \hline 
       C & 0 \end{array} \right]
    \right\} \, ds  
              \label{eq:4b} 
\end{eqnarray}
\end{subequations}

In multiline equations,
please pay attention to the message ``\verb+Overfull \hbox+'', 
and the equations should be composed with the proper length.

With the \verb+subequations+ environment, sub-equation numbers such as 
\Req{eq:4a}, \Req{eq:4b} can be achieved.
In equations, bold fonts can be output by using \verb+\mbf+ command.
The superscript ${\rm T}$ which expresses the transpose of a matrix and $\hinf$ 
can be achieved by \verb+\T+ and \verb+\hinf+ respectively.

For in-line equations, please use $\displaystyle \sum_{k=1}^N$
instead of $\sum_{k=1}^N$.
Similarly, the rule is applicable to \verb+\lim+, \verb+\max+, \verb+\min+,
etc.
For super and subscripts,
please use $X_a^b$ (\verb+$X_a^b$+) instead of ${X_a}^b$ (\verb+${X_a}^b$+).

\section{Figures and Tables}
%----------------------------
\begin{figure}[b]
        \centering
	\includegraphics[width=5cm,clip]{tmp.eps}
        \caption{Mass-spring-damper system}
        \label{fig:1}
\end{figure}
%----------------------------
%
%----------------------------
\setlength{\unitlength}{10mm}
%

\begin{figure}[b]
        \centering
%
        \begin{picture}(4.5,1)(0,0)
                \thicklines
                \put(0,0.5){\vector(1,0){1.5}}
                \linethickness{1.2pt}
                \put(1.5,0){\framebox(1.5,1){$G(s)$}}
                \thicklines
                \put(3,0.5){\vector(1,0){1.5}}
        \end{picture}
%
        \caption{Plant}
        \label{fig:2}
\end{figure}
%----------------------------
%
%----------------------------
\begin{figure}[b]
        \centering
%
        \begin{picture}(5.5,2.5)(0,0)
                \thicklines
                \put(0,2){\vector(1,0){0.85}}
                \put(0.7,2.2){\makebox(0,0){$ \scriptstyle + $}}
                \put(1,2){\circle{0.3}}
                \thicklines
                \put(1.15,2){\vector(1,0){0.85}}
                \linethickness{1.2pt}
                \put(2,1.5){\framebox(1.5,1){$G(s)$}}
                \thicklines
                \put(3.5,2){\line(1,0){1}}
                \put(4.5,2){\circle*{0.08}}
                \put(4.5,2){\vector(1,0){1}}
                \put(4.5,2){\line(0,-1){1.5}}
                \put(4.5,0.5){\vector(-1,0){1}}
                \linethickness{1.2pt}
                \put(2,0){\framebox(1.5,1){$H(s)$}}
                \thicklines
                \put(2,0.5){\line(-1,0){1}}
                \put(1,0.5){\vector(0,1){1.35}}
                \put(0.8,1.7){\makebox(0,0){$ \scriptstyle - $}}
        \end{picture}
%
        \caption{Feedback control system}
        \label{fig:3}
\end{figure}

Graphics files (EPS files) can be inserted into a manuscript by 
\verb+\includegraphics+ command of the {\tt graphicx} package
(see \rfig{fig:1}). 
Here are some examples to insert graphics into a manuscript.
The {\tt picture} environment is also available
to draw figures (see \rfig{fig:2,fig:3}).

%
\begin{table}[h]
  \centering
  \caption{Example of table ({\tt slashbox.sty})}
  \label{table:1}
        \vspace{0.5\baselineskip}
  \begin{tabular}{!l!*{2}{c|}c!}\hlinethick
  \backslashbox{Room}{Date}
    &\makebox[3em]{5/31} &\makebox[3em]{6/1} &\makebox[3em]{6/2}\\ \hlinethick
    Room A	& --- & --- & --- \\ \hline
    Room C12	& --- & --- & --- \\ \hline
    Room F1201	& --- & --- & --- \\ \hlinethick
  \end{tabular}
\end{table}
%

Here is an example of a table. 
In the {\tt scitrans.cls},
the \verb+\tabular+ command has been extended for the ISCIE format.
The \verb+\tabular+ command provides the thin and thick lines.
The thin line can be achieved by the traditional way: ``\verb+|+''
for the vertical line and ``\verb+\hline+'' for the horizontal line.
The thick line can be achieved by ``\verb+!+'' and ``\verb+\hlinethick+''
for the vertical and horizontal thick lines respectively.

The {\tt arydshln.sty} is included in the {\tt scitrans.cls}
so that dashed lines are also available. 
Examples are shown in \rtab{table:2,table:3}.

%----------------------------
\begin{table}[hbt]
        \centering
        \caption{Commands for reference}
        \label{table:2}

        \vspace{0.5\baselineskip}

        \hdashlinewidth=8pt
        \hdashlinegap=4pt
        \begin{tabular}{!c|l!} \hlinethick
                Definition  & \verb+\rdefinition+ \\ \hdashline
                Theorem     & \verb+\rtheorem+ \\ \hdashline
                Lemma       & \verb+\rlemma+ \\ \hdashline
                Proposition & \verb+\rproposition+ \\ \hdashline
                Corollary   & \verb+\rcorollary+ \\ \hdashline
                Example     & \verb+\rexample+ \\ \hlinethick
        \end{tabular}
\end{table}
%----------------------------
%
%
%----------------------------
\begin{table}[hbt]
        \centering
        \caption{Commands for reference to equations, figures and tables}
        \label{table:3}

        \vspace{0.5\baselineskip}

        \hdashlinewidth=2pt
        \hdashlinegap=2pt
        \begin{tabular}{!l|l!} \hlinethick
                Equation                 & \verb+\req+ \\ \hdashline
                Equation in appendices   & \verb+\Req+ \\ \hdashline
                Equation with sub-number & \verb+\Req+ \\ \hdashline
                Figure                   & \verb+\rfig+ \\ \hdashline
                Table                    & \verb+\rtab+ \\ \hlinethick
        \end{tabular}
\end{table}
%----------------------------

\section{Citations}
Citations can be made with the \verb+\cite+ command\cite{foo1}. 
The \verb+\cite*+ command automatically places a word ``Ref.''
before the reference number as ``\cite*{foo1}''.

The multiple citation such as
\verb+\cite{foo1,foo2}+ and \verb+\cite{foo2,foo3,foo4}+ 
achieves \mbox{}\cite{foo1,foo2} and \mbox{}\cite{foo2,foo3,foo4} respectively.

\section{Cross-Referencing}
In order to reference the definition, theorem etc.,
please use the commands listed in \rtab{table:2},
for example: \verb+\rtheorem{theorem:1}+, \verb+\rremark{remarl:1}+.

\rtheorem{theorem:1} is an example of the \verb+\rtheorem+ command.

\rremark{remark:1} is an example of the \verb+\rremark+ command.

For referencing the equation,
figure and table, please use the commands listed in \rtab{table:3}.
These commands automatically add appropriate words before reference numbers.
For example, 
%the commands \verb+\req{eq:1}+, \verb+\rfig{fig:1}+ and \verb+\rtab{table:1}+
achieve

\begin{itemize}
  \item \verb+\req{eq:1}+ $\quad\Longrightarrow\quad$ \req{eq:1}
  \item \verb+\rfig{fig:1}+ $\quad\Longrightarrow\quad$ \rfig{fig:1}
  \item \verb+\rtab{table:1}+ $\quad\Longrightarrow\quad$ \rtab{table:1}
\end{itemize}
The multiple referencing can be also achieved, for example,
\begin{itemize}
  \item \verb+\req{eq:1,eq:2,eq:3}+ $\quad\Longrightarrow\quad$
	\req{eq:1,eq:2,eq:3}
  \item \verb+\rfig{fig:1,fig:2}+ $\quad\Longrightarrow\quad$ \rfig{fig:1,fig:2}
  \item \verb+\rtab{table:1,table:2}+ $\quad\Longrightarrow\quad$
	\rtab{table:1,table:2}
\end{itemize}
In order to use the same format through the manuscript,
please do not use traditional 
\verb+\ref+ command.

\section{Others}
\subsection{Footnote}
The footnote is available with \verb+\footnote+ command%
\footnote{This is an example of the {\tt \textbackslash footnote} command.}.

\subsection{URL}
The {\tt scitrans.cls} provides the \verb+\url+ command to output a URL. 
For example, \url{http://www.iscie.or.jp/} can be achieved by 
\verb+\url{http://www.iscie.or.jp/}+. 
Also, {\tt \url{http://www.iscie.or.jp/}}  can be achieved by 
\verb+{\tt \url{http://www.iscie.or.jp/}}+.

\acknowledgement
The \verb+\acknowledgement+ command can be used to state the acknowledgements.

\begin{thebibliography}{9}
\bibitem{foo1}
        I.\ S.\ Cie: 
        The ISCIE style option; 
        {\it ISCIE Journal}, Vol.~0, No.~0, pp.~000--999 (1999)

\bibitem{foo2}
        R.\ E.\ Kalman: 
        A New Approach to Linear Filtering and Prediction Problems; 
        {\it Trans.\ of the ASME--J. of Basic Engineering}, Vol.~82 (Series D), 
        pp.~35--45 (1960)

\bibitem{foo3}
        A.\ Papoulis: 
        {\it Probability, Random Variables and Stochastic Processes}; 
        4th Edition, McGraw-Hill (2002)

\bibitem{foo4}
        Authors:
        Article title, {\it Book Title} (Editor(s), Ed(s).), Publisher,
        pp.~00--99 (1999)
\end{thebibliography}

%% Appendix
%
\appendix

This is an example of the \verb+\appendix+ command.
If there is only one section, please use \verb+\section*+ command. 
If there is more than one section, please use \verb+\section+ command.

\section{Equation in Appendix}
This is an example of \verb+\section+ command in the appendix. 
\begin{equation}
  u=Fx
\end{equation}

\section{Slash Line in Table}
In {\tt scitrans.cls}, {\tt slashbox.sty} is included so that slash 
lines are available in tables.
The followings are quoted from the manual of {\tt slashbox.sty} which is 
slightly modified for this document.

The usage is pretty straightforward, such as

\bigskip  %%Do not use this command in your manuscript.

\begin{tabular}{!l!*{3}{c!}}\hlinethick
\backslashbox{Room}{Date}
&\makebox[3em]{5/31}&\makebox[3em]{6/1}&\makebox[3em]{6/2}\\ \hlinethick
Room A&&&\\ \hline
Room C12&&&\\ \hline
Room F102&&&\\ \hlinethick 
\end{tabular}

\bigskip  %%Do not use this command in your manuscript.

\noindent
You may include a newline (\verb+\\+) in `Room' and/or `Date'.
Note that you will get spaces aside the slash line if there is a
wider column in the same column of a different line.
In such a case, you need to specify the width of the slashed column
by saying

\bigskip  %%Do not use this command in your manuscript.

\begin{tabular}{!l!*{2}{c!}} \hlinethick 
\backslashbox[40mm]{Room}{Date}
&\makebox[3em]{5/31}&\makebox[3em]{6/1}\\ \hlinethick 
Long Long Room Name&&\\ \hline
Room C12&&\\ \hline
Room F102&&\\ \hlinethick
\end{tabular}

\bigskip  %%Do not use this command in your manuscript.

The specified width is ignored if it is narrower than the natural
width of the column.

\verb+\(back)slashbox+ assumes by default that there is a blank space
of width \verb+\tabcolsep+ on both sides of the column.
Thus the slash line might exceed the boundary when you use \verb+@{}+ 
etc.

You can avoid it by specifying

\bigskip  %%Do not use this command in your manuscript.

\begin{tabular}{!@{\ $\bullet$\hspace*{3mm}}l!*{3}{c!}} \hlinethick 
\multicolumn{1}{!@{}l!}{\backslashbox[0pt][l]{Room}{Date}}
&\makebox[3em]{5/31}&\makebox[4em]{6/1}&\makebox[3em]{6/2}\\ \hlinethick
Room A&&&\\ \hline
Room C12&&&\\ \hline
Room F102&&&\\ \hlinethick 
\end{tabular}

\bigskip  %%Do not use this command in your manuscript.

\noindent
Here \verb+[l]+ tells the command that there is no extra space on the
left of this column.  You can use \verb+[r]+ and \verb+[lr]+ likewise.
You have to also specify the width of the column in this case, but it
can be 0pt.

\bigskip  %%Do not use this command in your manuscript.

\chosharyakureki

\authorbiography{Given-name, ,Family-name}{}{Member}{%
  Example of {\tt \textbackslash authorbiography}
  command. If you wish to include your photograph, please use this command.
  Please submit your photo after acceptance for publication.
  Please write down your biography here....
  Please write down your biography here....
  Please write down your biography here....
  Please write down your biography here....
  Please write down your biography here....
  Please write down your biography here....
  }

\authorbiography{Given-name, ,Family-name}{}{Non-Member}{%
  Example of {\tt \textbackslash authorbiography}
  command. If you wish to include your photograph, please use this command.
  Please submit your photo after acceptance for publication.
  Please write down your biography here....
  Please write down your biography here....
  Please write down your biography here....
  Please write down your biography here....
  Please write down your biography here....
  Please write down your biography here....
  }

\authorbiography*{Given-name, ,Family-name}{}{Member}{%
  Example of {\tt \textbackslash authorbiography$\ast$} command.
  If you do not wish to include your photograph, please use this command.
  Please write down your biography here....
  Please write down your biography here....
  Please write down your biography here....
  Please write down your biography here....
  }

### 2020-11-15 template/paper/paper_e.tex
Done-

@@
 \abstract{
-       A method to design the two-dimensional shapes of patterns of two piece brassiere cup is proposed when its target three-dimensional shape is given as a cloud of its data points.
-A brassiere cup consists of several patterns and their shapes are designed by repeatedly making a paper cup model and checking its three-dimensional shape.
-For improvement of design efficiency of brassieres, such trial and error must be reduced.
-As a cup model for check is made of paper not cloth, it is assumed that the surface of the model is composed of several developable surfaces.
-When two lines lying on a developable surface are given, the shape of the surface can be determined.
-Then, the two-piece brassiere cup can be designed by minimizing the error between the surface and given data points.
-It was mathematically verified that the original developable surface can be reproduced from data points on it by use of our proposed method.
+       A brassiere cup consists of several patterns.
+Traditionally, it is designed by repeatedly creating a paper cup model and verifying its three-dimensional (3D) shape.
+Reducing such trial and error will enhance the design efficiency.
+A method to partly automate the design of two-dimensional shapes in the patterns for a two-piece brassiere cup is proposed when the target 3D shape is given as a cloud of data points.
+It is assumed that the surface of the model is composed of several developable surfaces because the model is made of paper and not cloth.
+If two lines lying on a developable surface are given, the shape of the surface can be determined.
+Consequently, a two-piece brassiere cup can be designed by minimizing the error between the surface and the given data points.
+Here, we mathematically verify that our proposed method can reproduce the original developable surface.
 }
@@
 
-Developable surfaces that can be unfolded into a plane without expanding and contracting are widely used from shipbuilding to manufacturing of clothing, which are suitable to representation of surfaces that can be made of leather, paper, and sheet metal.
-In such fields, it is very important to design the two-dimensional shapes of plates which can form the required three-dimensional shape by being bent and joined.
+Developable surfaces can be unfolded into a plane without expanding or contracting.
+They are widely used in many industries from shipbuilding to manufacturing of clothing because they can represent surfaces made of leather, paper, or sheet metal.
+It is important to design two-dimensional (2D) shapes that form the required three-dimensional (3D) shape by bending and joining.
 In this paper, we focus on production of brassieres, which is related to design of two-dimensional shapes of plates.
-Brassieres are manufactured to meet various demands, such as to enhance a woman's breast size, to create cleavage, or to minimize breast movement.
-For this reason, the cup shape of a brassiere is very important when designing a brassiere.
+Brassieres are manufactured to meet various demands, such as to Herein we focus on the production of brassieres, which is related to the design of 2D shapes of plates.
+Brassieres are manufactured to meet various demands such as enhancing a woman’s breast size, creating cleavage, or minimizing breast movement.
+Due to these diverse demands, the cup shape is a critical element when designing a brassiere.
 A brassiere cup is formed by several pieces of cloth called patterns and a wire.
-For example, as shown in \rfig{fig:patterns}, a two-piece brassiere cup is composed of the upper pattern, the lower pattern and the lower line.
+Figure 1 shows an example of a two-piece brassiere cup composed of an upper pattern, lower pattern, and lower line.
 \begin{figure}[h!]
@@
 \end{figure}
- And the cup has three curves and they are also very important to design.
-As shown in \rfig{fig:TwoCurves}, one is the wire line corresponding to the boundary between a breast and a body.
-Another is the ridge line of the cup corresponding to the outline of a bust on a transverse plane.
-The other is the upper line to connect a cup and shoulder strap.
+ The three resulting curves are important to the design.
+The wire line corresponds to the boundary between the breast and body (\rfig{fig:TwoCurves}).
+The ridge line of the cup corresponds to the outline of a bust on a transverse plane, while the upper line connects the cup to the shoulder strap.
 
@@
 In apparel industries, the form of a product is fixed by fashion designers and pattern makers.
-Fashion designers draw an image of the product and pattern makers determine the shapes of patterns to meet various demands of the ideal shape, which previously mentioned about a brassiere, and so on.
+Fashion designers draw the product image, while pattern makers determine the pattern shapes to meet various demands of the ideal shape.
 %%fig
@@
 \end{figure}
-The design process of a brassiere cup is shown in \rfig{fig:process}.
-In design cite, pattern makers first consider the functional requirement of a brassiere cup based on a breast shape, then determine the pattern shape.
-Since this design procedure cannot mainly be performed by CAD system but based on experience and intuition, they must check the shapes with a paper model of the cup and modify them repeatedly to realize the function.
-So, the situation may cause unnecessary repetition of modifying and checking pattern shapes.
-In order to improve the design efficiency of brassieres, it is required to reduce such trial and error as much as possible.
-So, in this paper, we focus on the process srrounded by a dotted line in \rfig{fig:process} and aim to automate it.
-When it comes to the function of a brassiere cup, Higuchi researched what emphasis is placed on in design of a brassiere cup\cite{c1}.
-According to  \cite{c1}, the function: fitting breast is most important.
-Therefore, we propose a method to design the shapes of patterns of a brassiere cup fitting the given breast shape.
-The given three-dimensional breast shape is assumed to be given as a cloud of data points, which can be obtained easily by measurement.
+\rfig{fig:process} overviews the design process of a brassiere cup.
+Pattern makers first consider the functional requirement of a brassiere cup based on the breast shape, and then they determine the pattern shape.
+This design process is based on experience and intuition.
+Hence, pattern makers must verify the shapes with a paper model of the cup and repeatedly modify the shapes to realize the intended function.
+This process may cause unnecessary repetition.
+To improve the design efficiency of brassieres, trial and error should be minimized.
+Herein we strive to automate the steps indicated by the dotted line in \rfig{fig:process}.
+A previous study on the influence of design on the function of a brassiere cup found that fitting the breast has the largest impact\cite{c1}.
+Hence, this study proposes a method to design the pattern shapes of a brassiere cup to fit the given breast shape.
+Here, the given 3D breast shape is assumed to be a cloud of data points, which can be obtained easily by measurements.
 
@@
 %==============================================================%
+Because the cup shape is made by bending and sewing each pattern and is assumed to be inextensible, a cup model consists of several developable surfaces.
+With respect to modeling of developable surfaces, previously proposed modeling methods have focused on the geodesic line\cite{c2}, B-spline or NURBS surface\cite{c3,c4}, offsets of Bertrand curves, which coincide with each normal direction\cite{c5,c6}, and arbitrary curves\cite{c7}.
+Martin proposed a method to reconstruct a developable surface from its point clouds based on the Laguerre geometry\cite{c8}.
+Chen et al.
+proposed an algorithm to approximate a developable surface from its point cloud\cite{c9}.
+However, none of these methods reference the developed shape as they focus on a single developable surface.
+Manufacturing of a brassiere cup requires the pattern shapes (i.e., developed shapes of a cup) but not the 3D cup shape.
 
-As a cup shape is made by bending and sewing each pattern and assumed to be inextensible, the cup model consists of several developble surfaces.
-With respect to modeling of develoable surfaces, a method to model developable surface by focusing on the geodesic line\cite{c2}, B-spline or NURBS surface\cite{c3,c4}, offsets of Bartrand curves which coincide each normal direction\cite{c5,c6}, and arbitrary curves on it\cite{c7}.
-Especially, Martin proposed a method to reconstruct developable surface from its point clouds based on Laguerre geometry\cite{c8}.
-Also, Chen et al.
-proposed an algorithm to approximate developable surface from its point cloud\cite{c9}.
-However, all of them does not reference its developed shape and only focus on a single developable surface.
-When it comes to manufacturing a brassiere cup, the pattern shapes, i.e.
-developed shapes of a cup is required, not 3D cup shape.
-Especially in a study on brassieres, Wakamatsu et al.
-proposed a method to predict the three-dimensional shape of a paper cup model when the two-dimensional shape of pattern is given \cite{c10,c11}.
-As a result, evaluation of the patterns becomes possible without actually creating a paper model.
-However, repetitive modification of the patterns is still required to obtain the target three-dimensional shape of the cup.
+In a study on brassieres, Wakamatsu et al.
+proposed a method to predict the 3D shape of a paper cup model when the 2D shape of a pattern is given\cite{c10,c11}.
+Hence, patterns can be evaluated without actually creating a paper model.
+However, repetitive modification of the pattern is still required to obtain the target 3D shape of the cup.
 Ito et al.
 developed a paper model CAD system based on the theory of developable surfaces\cite{c12}.
-If a three-dimensional curve that means a sewn curve and a two-dimensional curve that means a piece to be sewn are given, a feasible region where the sewn surface does not intersect itself can be shown with this system.
-However, it is difficult to design the shape of patterns, that is, the shape of two-dimensional curves with this system.
-We previously proposed method to design pattern shape and its developable surface from two lines: a wire line and a ridge line.
-They are obtained by solving optimization problem whose design parameters are the geodesic curvatures of a pattern shape and objective function is the error between generatrices determined by the geodesic curvature of a lower edge and the wire line and generatrices determined by the geodesic curvature of an upper edge and the ridge line.
-However, when it apply to this problem, it is required to  solve this optimization problem until the intended shape\cite{MyRef}.
-It leads to taking unnecessary time.
+If a 3D curve, which means a sewn curve, and a 2D curve, which means a piece to be sewn, are given, this system can identify the feasible region where the sewn surface does not intersect itself.
+Unfortunately, it is difficult to design the pattern shapes.
+That is, determining the shape of 2D curves is challenging with this system.
+We previously proposed a method to design the pattern shape and its developable surface from two lines: a wire line and a ridge line.
+These lines are obtained by solving the optimization problem when the design parameters are the geodesic curvatures of a pattern shape and the objective function is the error between generatrices determined by the geodesic curvature of a lower edge and the wire line and generatrices determined by the geodesic curvature of an upper edge and the ridge line.
+However, the previously proposed method requires an iterative process to solve the optimization problem for the intended shape\cite{c13}, which is time-consuming.
+Brassiere patterns are typically comprised of two or three pieces.
+Herein we focus on a two-piece brassiere cup, and we propose a design method to improve the design efficiency when a cloud of its data points is given.
+
 %==============================================================%
-
-The products are mainly composed of two or three pieces of pattern.
-In this paper, we focus on two-piece brassiere cup and aim to propose a method to design its pattern shapes toward improvement of its design efficiency when a cloud of its data points is given.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-In this section, we aim to explain numerical expression of a developable surface. 
-When it comes to a curvature of a space curve on a surface, it is divided to the normal curvature by deforming the surface and the geodesic curvature by deforming a space curve.
-The geodesic curvature does not change by deforming the surfce as long as it is not stretched.
-In case of a brassiere cup, the normal curvature can be manipulated by deforming the surface, but the geodesic curvature cannot.
-So, it is required to design the geodesic curvature in order to coincide a space curve with a boundary of the developable surface.
-Let \textit{lower edge} be the curve connecting to a lower wire as shown Fig.\ref{fig:pattern_L}, and \textit{upper edge} be the curve combining with upper cup as shown Fig.\ref{fig:pattern_L}.
-In this section, we aim to propose a method to determine a developable surface by two curves that lie on it and to design the pattern shape from them.
-We explain the method to express the developable surface from parameters of a space curve , the condition of two lines that lie on the developable surface, and a pattern shape obtained from them.
-For this aim, we set object coordinate system on the lower edge of the cup surface as shown \rfig{fig:obj_coord} so that $\zeta$ -axis always coincides the tangential direction of the edge line and $\eta$ -axis always coincides the normal direction of the surface.
-The posture of the object coordinate system is changed by deformation of the cup.
-Then, the infinitesimal displacement vector of each axial direction can be described by the infinitesimal rotational ratio vector $ \mbold{\omega} = \left[\omega_{\xi}\;\;\omega_{\eta}\;\;\omega_{\zeta}\right]^{\mathrm{T}}$as follows:
+This section explains the numerical expressions of a developable surface.
+The curvature of a space curve on a surface can be divided into two: the normal curvature and geodesic curvature.
+The former is realized by deforming the surface, while the latter is realized by deforming a space curve.
+Deforming the surface does not change the geodesic curvature as long as the surface is not stretched.
+In the case of a brassiere cup, only the normal curvature can be manipulated by deforming the surface.
+Because the geodesic curvature cannot be manipulated by deforming the surface, it must be designed such that the space curve coincides with a boundary of the developable surface.
+Here, we propose a method to determine a developable surface using two curves that lie on the surface and design a pattern shape.
+Consider the case where the \textit{lower edge} is the curve connecting the lower wire (\rfig{fig:pattern_L}) and the \textit{upper edge} is that combining the upper cup (\rfig{fig:pattern_U}).
+Our method expresses the developable surface using the parameters of a space curve, the condition of two lines that lie on the developable surface, and their obtained pattern shape.
+\rfig{fig:obj_coord} depicts the object coordinate system on the lower edge of the cup surface, where the $\zeta$-axis always coincides with the tangential direction of the edge line and the  $ \eta $-axis always coincides with the surface normal direction.
+Deformation of the cup changes the posture of the object coordinate system.
+Thus, the infinitesimal displacement vector of each axial direction can be described by the infinitesimal rotational ratio vector $ \mbold{\omega} = \left[\omega_{\xi}\;\;\omega_{\eta}\;\;\omega_{\zeta}\right]^{\mathrm{T}}$ as
 
@@
 \end{equation}
-where a prime means a derivative of $s$, and $\mbold{\Omega}(\mbold{\omega})$ is represented as follows: 
+where a prime means a derivative of $s$, and $\mbold{\Omega}(\mbold{\omega})$ is represented as
 \begin{equation}
@@
 
-Then, the tangent vector is expressed as follows: 
+Then, the tangent vector is expressed as 
 \begin{equation}
@@
 \end{equation}
-where $\zetavec_0$ represents the tangent vector at $s=0$ and by integrating \req{eq:zetav_eq}, the position of the curve can be calculated as follows:
+where $\zetavec_0$ represents the tangent vector at $s=0$. By integrating \req{eq:zetav_eq}, the position of the curve can be calculated as
 \begin{equation}
@@
 \end{equation}
-where $\mbold{x}_0$ means the position at $s=0$.
+where $\mbold{x}_0$ indicates the position at $s=0$.
 
@@
 
-First, we explain numerical expression of developable surface by the constraint of Gaussian curvature. 
-In general, a normal curvature of a direction vector $\mbold{d}_{\theta} = \zetavec \cos \theta + \xivec \sin \theta $ can be described using coefficients of the first and the second fundamental forms $E, F, G, L, M$ and $N$:
+First, consider the numerical expression of a developable surface constrained by a Gaussian curvature.
+In general, the normal curvature of a direction vector $\mbold{d}_{\theta} = \zetavec \cos \theta + \xivec \sin \theta $ can be described using coefficients of the first and the second fundamental forms $E, F, G, L, M$ and $N$ as
 \begin{equation}\label{eq:def_kappa_theta}
@@
 \end{equation}
-And the Gaussian curvature $K$ and the mean curvature $H$, which characterize a surface, can be defined as extreme values of \req{eq:def_kappa_theta}: $ \kappa_{\max} $ and $ \kappa_{\min} $ as follows
+Then the Gaussian curvature $K$ and the mean curvature $H$, which characterize a surface, can be defined as extreme values of \req{eq:def_kappa_theta}: $ \kappa_{\max} $ and $ \kappa_{\min} $ as
 
@@
 
-In this paper, coefficients of first fundamental form are represented as following equation:
+Here, the coefficients of the first fundamental form are represented as
 \begin{equation}
@@
 \end{equation}
-Also, coefficients of second fundamental form are represented as following equation:
+In addition, the coefficients of the second fundamental form are represented as
 \begin{equation}
@@
 \end{equation}
-Then, Gaussian curvature $K$ and the mean curvature $H$ are described by
-the following equation:
+Then Gaussian curvature $K$ and the mean curvature $H$ are described by the following equations
 
@@
 \end{eqnarray}
-Developable surface is defined as the surface whose Gaussian curvature $K = 0$, which means $\kappa_{\min}=0$.
-Then, the mean curvature can be calculated as $2H=\kappa_{\max}$.
-This means that a line direction of which coincides with direction $\mbold{d}_{\min}$ is kept straight after deformation.
+A developable surface is defined as a surface with a Gaussian curvature $K = 0$.
+That is $\kappa_{\min}=0$.
+TThus, the mean curvature can be calculated as $2H=\kappa_{\max}$.
+The line direction coinciding with the direction $\mbold{d}_{\min}$ remains straight after a deformation.
 This straight line is referred to as a generatrix.
-In this paper, principal directions are described by using the angle $ \alpha $: 
+In this paper, the principal directions are described using the angle $ \alpha $ as
 \begin{eqnarray}\label{eq:d1d2_eq}
@@
 The angle $ \alpha $ is referred to as the \textit{rib angle} in this paper.
-By solving $ \kappa_{\theta} = 0 $,　the rib angle $ \alpha $ can be calculated as following equation:
+By solving $ \kappa_{\theta} = 0 $,　the rib angle $ \alpha $ can be calculated as
 \begin{equation}\label{eq:alpha_eq}
@@
 \end{equation}
-And from \req{eq:GC_expressed_omega}, $\kappa_1$ is calculated as follows: 
+From \req{eq:GC_expressed_omega}, $\kappa_1$ is calculated as 
 \begin{equation}\label{eq:kappa1_eq}
@@
 
-Next, we explain the constraint of developable surface when two curves that lie on the surface are given.
+Next, consider the constraint of a developable surface when two curves lie on the surface.
 Let $s_a$ and $s_b$ be the arc length and $\mbold{x}_a(s_a)$, $\mbold{x}_b(s_b)$ be positions of each curve.
 We assume that these curves have ${\rm C}^2$ community at least.
-In general developable surfaces are a special kind of ruled surfaces.
-When the surface is a ruled surface, a generatrix $ \mbold{g} $ is described as follows:
+In general, developable surfaces are a special kind of ruled surface.
+When a surface is a ruled surface, the generatrix $ \mbold{g} $ is described as
 
@@
 
-Note that $s_a$ can take an arbitrary value against $ s_b $. Therefore, the variation of a generatrix $ \Delta \mbold{g} $ is described by total differential form as follows:
+Note that $s_a$ can take an arbitrary value against $ s_b $. Therefore, the variation of a generatrix $ \Delta \mbold{g} $ is described by total differential form as
 \begin{equation}
@@
 where $ \zetavec_a$ and $\zetavec_b $ are tangent vectors of $ \mbold{x}_a $ and $ \mbold{x}_b $, respectively.
-Next, let $ \Theta $ be the infinitesimal plane surrounded by four vectors $ \zetavec_a \Delta s_a, \zetavec_b \Delta s_b,\mbold{g}$, and $\mbold{g}+\Delta \mbold{g} $ as shown in \rfig{fig:Theta}.
+Next, let $ \Theta $ be the infinitesimal plane surrounded by four vectors $ \zetavec_a \Delta s_a, \zetavec_b \Delta s_b,\mbold{g}$, and $\mbold{g}+\Delta \mbold{g} $ (\rfig{fig:Theta}).
 When the ruled surface is a developable surface, the plane $ \Theta $ is a tangent plane without twisting.
@@
 \det (\zetavec_a, \mbold{g}, \mbold{g}+\Delta \mbold{g})=0
+\label{eq:det_developeq}
 \end{equation}
-By solving it, the following equation is obtained:
+Solving \req{eq:det_developeq} gives
 \begin{equation}
@@
 \end{figure}
-It indicates that the arc length of each curve is subordination.
+\req{eq:Cond1} indicates that the arc length of each curve is subordination.
 When two curves are corresponded to edge lines and $s_b$ can be expressed as $s_b(s_a)$, $\mbold{d}_{\min}\equiv\frac{\mbold{g}}{|\mbold{g}|}$ is established.
@@
 \end{equation}
-Using $\mbold{d}_{\min}$ and $\alpha$, $\mbold{\omega}$ can be represented as following equation:
+Using $\mbold{d}_{\min}$ and $\alpha$, $\mbold{\omega}$ can be represented as
 \begin{equation}\label{eq:omegaVec}
@@
 
-Next, we explain how to determine the pattern shape from the developable surface.
-The planar curve generated by developing the space curve $ \mbold{x}_a $ is defined a the lower curve and that by developing the space $ \mbold{x}_b $ is defined as the upper curve.
-
-We set developed planar coordinate system $ vw $ so that $ v $-axis always coincides the line AB as shown in \rfig{fig:PatternImage}.
+Now let’s consider how to determine the pattern shape from a developable surface.
+The planar curve generated by developing the space curve $ \mbold{x}_a $ is defined as the lower curve, whereas that generated by developing the space $ \mbold{x}_b $ is defined as the upper curve.
+\rfig{fig:PatternImage} shows the developed planar coordinate system $ vw $ so that $ v $-axis always coincides the line AB.
 Let $ \mu_a $ be the angle between the tangential direction of the lower edge and the $ v $-axis.
-$ \mu_a $ is obtained as follows when the curvature of the lower curve $ \omega_{\eta_a} $  is given:
+If the curvature of the lower curve $ \omega_{\eta_a} $ is given, $ \mu_a $ is obtained as
 \begin{equation}\label{eq:mu_eq}
@@
 \end{equation}
-where $ \mu_0 $ represents the angle of the lower edge at $ s=0 $ and is described later. From \req{eq:mu_eq}, the planar position $ \mbold{x}_{ae} $ is described as follows:
+where $ \mu_0 $ represents the angle of the lower edge at $ s=0 $, which is discussed later. From \req{eq:mu_eq}, the planar position $ \mbold{x}_{ae} $ is described as
 \begin{equation}\label{eq:x_LE}
@@
 Let $ \mbold{x}_{be} $ be the planar position of an upper edge.
-Since the rib angle of a pattern $ \alpha_a $ and the length of a generatrix of a pattern $ |\mbold{g}| $ don't change by being developed, $ \mbold{x}_{be} $ can be calculated as follows:
+Since the rib angle of a pattern $ \alpha_a $ and the length of a generatrix of a pattern $ |\mbold{g}| $ do not change by being developed, $ \mbold{x}_{be} $ can be calculated as
 \begin{equation}\label{eq:x_UE}
@@
 \end{equation}
-From above, a developed shape can be obtained when two curves that lie on the developable surface are given.
+From above, a developed shape can be obtained when two curves, which lie on the developable surface, are given.
 \begin{figure}[thpb]
@@
 \end{figure}
-\section*{EXPRESSION OF DESIGN PROCESS AS OPTIMIZATION PROBLEM}
-From section2, the cup shape can be determined by three curves: a wire wire, a ridge line and an upper line.
-Therefore, when a wire line is given, the objective of our study can be achieved by designing parameters of a ridge line and an upper line, which minimize the degree of fitting to the 3D breast shape.
-So, in this section, we aim to formulate this degree.
+\section*{EXPRESSION OF THE DESIGN PROCESS AS AN OPTIMIZATION PROBLEM}
+From section 2, the cup shape can be determined by three curves: a wire line, a ridge line, and an upper line.
+If the wire line is given, designing the parameters for the ridge and upper lines such that the degree of fitting to the 3D breast shape is minimized will enhance the design efficiency.
+This section formulates the optimization problem that our proposed method aims to solve.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection*{Formulation of the error between a point and a surface}
-In order to formulate the degree of fitting to the 3D ideal shape, we formulate the error between a point and a surface.
-In general, the position $\mbold{X}(s,t)$ of developable surface $S$ is expressed as following equation:
+To formulate the degree of fitting to a 3D ideal shape, we formulate the error between a point and a surface. In general, the position $\mbold{X}(s,t)$ of a developable surface $S$ is expressed as
 \begin{equation}\label{eq:Sur_eq}
@@
 \end{equation}
-The distance $\varepsilon(\mbold{p})$ between a point $\mbold{p}$ and a developable surface is formulated by the difference vector $\mbold{\delta}=\mbold{p}-\mbold{X}(s,t)$ as follows:
-
+The distance $\varepsilon(\mbold{p})$ between a point $\mbold{p}$ and a developable surface is formulated by the difference vector $\mbold{\delta}=\mbold{p}-\mbold{X}(s,t)$ as
 \begin{equation}\label{eq:eps_eq}
@@
 \end{equation}
-
-When a set of surface parameters $ (s^*,t^*) $ satisfies to minimize \req{eq:eps_eq}, $\mbold{\delta}$ is parallel to $ \etavec $. Therefore, the following equations are satisfied:
+When a set of surface parameters $ (s^*,t^*) $ satisfies to minimize \req{eq:eps_eq}, $\mbold{\delta}$ is parallel to $ \etavec $. Therefore, the following equations are satisfied
 \begin{equation}\label{eq:d_mindoteq}
@@
 \end{equation}
-
 \begin{equation}\label{eq:d_maxdoteq}
@@
 \end{equation}
-By solving \req{eq:d_mindoteq}, $ t^* $ is described as follows:
-
+By solving \req{eq:d_mindoteq}, $ t^* $ is described as
 \begin{equation}\label{eq:t*_eq}
@@
 \end{equation}
-By using \req{eq:t*_eq} and solving \req{eq:d_maxdoteq}, $ s^* $ is determined.
+By using \req{eq:t*_eq} and solving \req{eq:d_maxdoteq}, $ s^* $ can be determined.
 
-Let $ s_w,s_r,s_u $ be arc lengths of a lower wire, ridge line, and upper line and $ \mbold{\omega}_W (s_w ),\mbold{\omega}_R (s_r ),\mbold{\omega}_U (s_u ) $ be vectors to characterize each of them.
+Let $ s_w,s_r,s_u $ be the arc lengths of the lower wire, ridge line, and upper line and let $ \mbold{\omega}_W (s_w ),\mbold{\omega}_R (s_r ),\mbold{\omega}_U (s_u ) $ be vectors to characterize each of them, respectively.
 From \req{eq:Cond1}, $ s_r,s_u $ can be expressed as functions of $ s_w $: $ s_r (s_w ),s_u (s_w ) $.
 As mentioned, a two-piece brassiere cup is composed of two developable surfaces $ S_L $ and $ S_U $.
-Let $ D $ be the set of coordinates of points on a breast, $ D_L = \{\mbold{p}_{L,i} \in D \} $ be the set of points to evaluate the surface $ S_L $, and $ D_U = \{\mbold{p}_{U,i} \in D \} $ be the set of points to evaluated the surface $ S_U $, respectively.
+Let $ D $ be a set of coordinates of points on a breast, $ D_L = \{\mbold{p}_{L,i} \in D \} $ be a set of points to evaluate the surface $ S_L $, and $ D_U = \{\mbold{p}_{U,i} \in D \} $ be a set of points to evaluated the surface $ S_U $.
 Note that $ D_U = D \backslash D_L $.
@@
 
-First, \req{eq:d_mindoteq,eq:d_maxdoteq,eq:t*_eq}, the nearest surface parameters $ (s_w^*, t_w^*) $ of the lower cup to the point $ \mbold{p}_k $ can be derived.
+First, using \req{eq:d_mindoteq,eq:d_maxdoteq,eq:t*_eq}, the nearest surface parameters $ (s_w^*, t_w^*) $ of the lower cup to the point $ \mbold{p}_k $ can be derived.
 Then, the nearest point $ \mbold{X}(s^*, t^*) $ on the lower cup surface to the point $ \mbold{p}_k $ can be derived.
@@
 \end{equation}
-By finding two developable surfaces minimizing the error described by \req{eq:Lambda_eq}, appropriate pattern shapes can be determined.
+By finding two developable surfaces that minimize the error described by \req{eq:Lambda_eq}, the appropriate pattern shapes can be determined.
 
 \subsection*{Formulation of Objective Function and Conditions}
-Let us consider the conditions of this optimization.
-First, we explain the conditions about parameters of the ridge line and the upper line.
-When it comes to designing the space curve, $ \omega_{\zeta} $ does not affect its shape.
-Therefore, the following conditions are added:
+To consider the optimization conditions, we first explain the conditions for the parameters of the ridge line and the upper line.
+$ \omega_{\zeta} $ does not affect the shape of the space curve.
+Therefore, the following conditions are added
 \begin{eqnarray}\label{eq:conds_omgZt}
@@
 \end{eqnarray}
-
-When it comes to designing their arc length, the following  conditions  must be satisfied:
+Then the following conditions must be satisfied to design the arc length
 \begin{equation}\label{eq:conds_arc1}
@@
 \end{equation}
-In general, the end positions of the ridge line and the upper line are aligned to the end point of the wire line. Therefore, the following equations must be satisfied:
+In general, the end positions of the ridge and upper lines are aligned to the end point of the wire line. Therefore, the following equations must be satisfied 
 \begin{equation}\label{eq:conds_endp1}
@@
 
-In order to guarantee $ S_L $ and $ S_U $  are developable surfaces, the following equations must be satisfied:
+To guarantee that $ S_L $ and $ S_U $  are developable surfaces, the following equations must be satisfied 
 \begin{equation}\label{eq:conds_DevSur1}
@@
 \end{equation}
-Next, let us consider a “fuzzy” condition of a brassiere cup. 
-The upper line has a point to be connected with a shoulder strap.
-In this paper, we call this point \textit{connection point}.
-In design process, this point is usually not given as a unique condition, but a fuzzy condition.
+Next, consider a “fuzzy” condition for a brassiere cup. The upper line has a point where it is connected with the shoulder strap. Hereafter, this point is called the connection point. 
 \begin{figure}[!h]
@@
 \end{figure}
-It may cause unexpected error of the optimization problem. Therefore, we propose the following equation to deal with this fuzzy condition $ y \simeq Y $:
+Typically, this point is given as a fuzzy condition in the design process.
+This can lead to an unexpected error in the optimization problem.
+Therefore, we propose the following equation to deal with this fuzzy condition $ y \simeq Y $:
 \begin{equation}\label{eq:FuzzyEq}
@@
 \end{equation}
-where $ k_1 $ and $ k_2 $ are the variables to adjust a range of satisfying this condition.
-By adding this equation to the objective function, the fuzzy condition can be dealt.
-In this paper, we assumed that the position $ \mbold{X}_C $ to connect the upper line and the shoulder strap is given.
-Then, the objective function $ V $ is described as follows:
+where $ k_1 $ and $ k_2 $ are the variables to adjust the range that satisfies this condition.
+By adding this equation to the objective function, the fuzzy condition can be handled.
+Here, we assume that the position $ \mbold{X}_C $ to connect the upper line and the shoulder strap is given.
+Then the objective function $ V $ is described as
 \begin{equation}\label{eq:ObjectFunc}
@@
 where $\mbold{e}_0 $ ,$\mbold{e}_1 $ and $\mbold{e}_2 $ are represented as unit vectors of $ x $,$ y $ and $ z $-axis.
-By solving this optimization under the constraints, the shape of the brassiere cup, satisfying to fit data points of a breast, can be obtained.
+Solving this optimization under these constraints can provide the shape of the brassiere cup to fit the data points of a breast.
 
-\subsection*{A Procedure of Solving Optimization Problem}
-Let us explain a procedure of solving this optimization problem.
-First, we explain how to eliminate the condition.
-In order to satisfy \req{eq:conds_arc1,eq:conds_arc2,eq:conds_arc3,eq:conds_arc4}, $ s_r (s_w),s_u (s_w) $ are described using arbitrary functions $ \upsilon_r(s_w),\upsilon_u(s_w) $ as follows:
+\subsection*{Procedure to Solve the Optimization Problem}
+Prior to explaining the procedure to solve the optimization problem, we explain how to eliminate the condition.
+To satisfy  \req{eq:conds_arc1,eq:conds_arc2,eq:conds_arc3,eq:conds_arc4}, $ s_r (s_w),s_u (s_w) $ are described using arbitrary functions $ \upsilon_r(s_w),\upsilon_u(s_w) $ as
 \begin{eqnarray}
@@
 \end{eqnarray}
-When we assume that the initial position of the wire line, that of the ridge line, and that of the upper line are aligned, $ s_{r_0}=s_{u_0}=0 $.
+The initial position is assumed to be the wire line.
+Then the ridge and upper lines are aligned such that $ s_{r_0}=s_{u_0}=0 $.
 Let a composite function of $ s_r(s_w) $ and arbitrary function $ g(s_r) $ be defined as $ \tilde{g}(s_w) $, and a composite function of $ s_u (s_w ) $ and arbitrary function $ g(s_w) $ be defined as $ \hat{g}(s_w) $.
-Then, from \req{eq:ObjSys}, the object coordinate system of the ridge line and upper line can be expressed as follows:
+From \req{eq:ObjSys}, the object coordinate system of the ridge and upper lines can be expressed as
 \begin{equation}\label{eq:tildeobj}
@@
 \end{equation}
-and the position $ \mbold{x}_R(s_r) \equiv \tilde{\mbold{x}}_R(s_w) $ and $ \mbold{x}_U(s_u) \equiv \hat{\mbold{x}}_U(s_w) $ are expressed by the following equations:
+and the position $ \mbold{x}_R(s_r) \equiv \tilde{\mbold{x}}_R(s_w) $ and $ \mbold{x}_U(s_u) \equiv \hat{\mbold{x}}_U(s_w) $ are expressed by the following equations
 \begin{eqnarray}
@@
 Let $ \mbold{\psi} = [\omega_{\xi} \;\; \omega_{\eta} \;\; \upsilon] $ be the function vector of a line.
-Then, the vector of the ridge line $ \mbold{\psi}_R $ and the vector of the upper line $ \mbold{\psi}_U $ are represented using Ritz method\cite{c13} as follows:
+Then the vector of the ridge line $ \mbold{\psi}_R $ and the vector of the upper line $ \mbold{\psi}_U $ are represented using Ritz method\cite{c13} as
 \begin{equation}\label{eq:R_eq}
@@
 where $ \mbold{e}_i(s) $ is composed of trigonometric functions with different periods.
-And let $ \mbold{\Phi}_0 = [\xivec_0^\mathrm{T} \;\; \etavec_0^\mathrm{T} \;\; \zetavec_0^\mathrm{T}] $ be an initial basis of the objective coordinate system.
+Let $ \mbold{\Phi}_0 = [\xivec_0^\mathrm{T} \;\; \etavec_0^\mathrm{T} \;\; \zetavec_0^\mathrm{T}] $ be the initial basis of the objective coordinate system.
 
-From above, the objective function expressed as \req{eq:ObjectFunc} and geometric constraints expressed as \req{eq:conds_endp1,eq:conds_endp2,eq:conds_DevSur1,eq:conds_DevSur2} are described by the following total parameter vector:
+From above, the objective function, which is expressed as \req{eq:ObjectFunc}, and the geometric constraints, which are expressed as  \req{eq:conds_endp1,eq:conds_endp2,eq:conds_DevSur1,eq:conds_DevSur2} are described by the following total parameter vector
 \begin{equation}\label{eq:TotalCoefs}
@@
 
-Consequently, this problem can be converted to a non-linear programming problem.
-It is solved by the multiplier method and Nelder-Mead method in this paper.
-By solving the above problem, we can design the entire shape of a two-piece brassiere cup.
+Consequently, this problem can be converted into a nonlinear programming problem, which is solved using the multiplier method and Nelder-Mead method in this study.
+By solving the nonlinear programming problem, we can design the entire shape of a two-piece brassiere cup.
 
 \section*{SIMULATION AND VERIFICATION}
-In this section, we aim to consider the simulation result and verification of our proposed method.
-For this verification, the inﬁnitesimal rotational ratios vector $ \mbold{\omega}_W $ of the wire line was given as follows:
+To demonstrate the utility of our method, we conducted simulations and a verification. For the verification, the infinitesimal rotational ratios vector   of the wire line is given as
 \begin{equation}\label{eq:vrf_omgW}
@@
 \end{equation}
-and, the connection point $ \mbold{X}_C $ was given as follows: 
+while the connection point $ \mbold{X}_C $ is given as 
 \begin{equation}\label{eq:givenXc}
@@
 We prepared two examples of the simulation.
+Case (1) is a point cloud on a sphere whose radius is set on R by a uniform random number.
+Case (2) is a point cloud on a set of a developable surface by a uniform random number using \req{eq:Sur_eq}.
+The simulations aim to verify whether a two-piece brassiere cup can be designed to approximate an undevelopable surface that manifests the function of “fitting to a breast” and to confirm that the propose method recreates a given shape.
+Here, a uniform random number was generated by numpy.random() of Python.
+\rfig{fig:ObtainedSurfaceNDS}shows the obtained shape and input data for Case (1), where the solid line represents the given wire line.
+Each dotted line denotes the calculated generatrices of the cup shape, and each dot represents a data point.
+\rfig{fig:ObtainedSurfaceDS}shows the obtained pattern where the solid and dotted lines denote the lower and upper edges, respectively.
+Our proposed method produces a cup shape that manifests the function of “fitting to a breast”.
 
-Case (1): a point cloud on the sphere whose radius is set on R by uniform random number.
+ \rfig{fig:ObtainedSurfaceDS_Pat}. In \rfig{fig:ObtainedSurfaceDS_Pat}, a solid line and a dotted line represent as same as case(1).
 
-Case (2): a point cloud on the set of developable surface by uniform random number using \req{eq:Sur_eq}.
-
-And we aim to confirm two matters by them.
-\begin{enumerate}
-	\item to design the two-piece brassiere cup which can approximate undevelopable surface, which means it menifests the function: fitting to a breast".
-	\item to recreate the same shape that of given shape.
-\end{enumerate}
-In this study, uniform random number was generated by numpy.random() of Pyhton. At first, we show the result in case(1).
-
-As shown in \rfig{fig:ObtainedSurfaceNDS}, the solid line represents the given wire line, each dotted line does calculated generatrices of the cup shape, and each dots does the given data points.
-And the pattern shapes were calculated as shown in \rfig{fig:ObtainedSurfaceNDS_Pat}.
+\rfig{fig:ObtainedSurfaceNDS_Pat}.
 In \rfig{fig:ObtainedSurfaceNDS_Pat}, each solid line represents a lower edge and a dotted line represents an upper edge.
 In this result, we could confirm that the designed cup shape by our proposed method menifests the function:"fitting to a breast".
-Next, we show the result in case(2).
-In \rfig{fig:ObtainedSurfaceDS}, the solid line, each dotted line and dot represent as same as case(1).
-And the pattern shapes were calculated as shown in \rfig{fig:ObtainedSurfaceDS_Pat}.
-In \rfig{fig:ObtainedSurfaceDS_Pat}, a solid line and a dotted line represent as same as case(1).
-
+Next, we show the result in case(2). In
 As the calculated shapes approximate the given points, we conclude our proposed method in this paper is useful for efficient design of paper patterns of a two-piece brassiere cup.

### 2020-11-23 template/paper/paper_e.tex
Commit1123

@@
 %\usepackage{graphicx}
+\usepackage{color}
 \usepackage{math}
 \usepackage{bm}
-\usepackage[dvipdfmx]{graphicx,xcolor}
+%\usepackage[dvipdfmx]{graphicx,xcolor}
 \usepackage[dvipdfmx]{epsfig}
@@
 
+\chcolor{In a study to approximate developable surface, Yang et al.
+proposed a method to approximate surface with meshes composed of planar quadrilaterals\cite{cX1} and Odeo et al.
+proposed a method to define the developability of triangle meshes and appoximate them by a set of developable surfaces\cite{cX2}, and Martin et al.
+proposed a method to reconstruct surfaces by curved forming\cite{cX3}.
+But all of them only focus on approximating surface by developable surface, which means that they do not refer to the condition of a developable surface itself.
+When designing a brassiere, it is required to satisfy some conditons of a brassiere cup that designers intend.}
+
 In a study on brassieres, Wakamatsu et al.
@@
 \end{equation}
-Then the Gaussian curvature $K$ and the mean curvature $H$, which characterize a surface, can be defined as extreme values of \req{eq:def_kappa_theta}: $ \kappa_{\max} $ and $ \kappa_{\min} $ as
+Then the Gaussian curvature $K$ and the mean curvature $H$, which characterize a surface, can be defined as extreme values of \req{eq:def_kappa_theta}: $ \kappa_{\max} $ and $ \kappa_{\min} $ as follows\cite{cX4}
 
@@
 From above, a developable surface can be determined by $\mbold{\omega}$.
-%%%%%%%%%%%%%%ここまで7/21
 
@@
 
-Let $ \mbold{\psi} = [\omega_{\xi} \;\; \omega_{\eta} \;\; \upsilon] $ be the function vector of a line.
-Then the vector of the ridge line $ \mbold{\psi}_R $ and the vector of the upper line $ \mbold{\psi}_U $ are represented using Ritz method\cite{c13} as
+\chcolor{From above, a curve can be determined by $ \omega_{\xi} ,\omega_{\eta}$ and $\upsilon$.} Let $ \mbold{\psi}$ be a set of functions of $[\omega_{\xi} \;\; \omega_{\eta} \;\; \upsilon] $.
+\chcolor{Then a set of functions of the ridge line $ \mbold{\psi}_R $ and a set of functions of the upper line $ \mbold{\psi}_U $ are parameterized by using Ritz method\cite{c13} as}
 \begin{equation}\label{eq:R_eq}
-\mbold{\psi}_R = \left[ \begin{array}{ccc} \mbold{a}_{\omega_{\xi_R}}& \mbold{a}_{\omega_{\eta_R}}& \mbold{a}_{\upsilon_R} \end{array} \right] \cdot \mbold{e}(s_w) = \mbold{a}_R \cdot \mbold{e}(s_w) 
+\mbold{\psi}_R = \left[ \begin{array}{ccc} \mbold{a}_{\omega_{\xi_R}} \cdot \mbold{e}(s_w) & \mbold{a}_{\omega_{\eta_R}} \cdot \mbold{e}(s_w)& \mbold{a}_{\upsilon_R} \cdot \mbold{e}(s_w) \end{array} \right]
 \end{equation}
@@
 \begin{equation}\label{eq:U_eq}
-\mbold{\psi}_U = \left[ \begin{array}{ccc} \mbold{a}_{\omega_{\xi_U}}& \mbold{a}_{\omega_{\eta_U}}& \mbold{a}_{\upsilon_U} \end{array} \right] \cdot  \mbold{e}(s_w) = \mbold{a}_U \cdot \mbold{e}(s_w)
+\mbold{\psi}_U = \left[ \begin{array}{ccc} \mbold{a}_{\omega_{\xi_U}} \cdot  \mbold{e}(s_w) & \mbold{a}_{\omega_{\eta_U}} \cdot  \mbold{e}(s_w) & \mbold{a}_{\upsilon_U} \cdot  \mbold{e}(s_w)  \end{array} \right]
 \end{equation}
@@
 
-Consequently, this problem can be converted into a nonlinear programming problem, which is solved using the multiplier method and Nelder-Mead method in this study.
+Consequently, this problem can be converted into a nonlinear programming problem of $ \mbold{a} $, which is solved using the multiplier method and Nelder-Mead method in this study.
 By solving the nonlinear programming problem, we can design the entire shape of a two-piece brassiere cup.
@@
 \end{equation}
-We prepared two examples of the simulation.
-Case (1) is a point cloud on a sphere whose radius is set on R by a uniform random number.
-Case (2) is a point cloud on a set of a developable surface by a uniform random number using \req{eq:Sur_eq}.
-The simulations aim to verify whether a two-piece brassiere cup can be designed to approximate an undevelopable surface that manifests the function of “fitting to a breast” and to confirm that the propose method recreates a given shape.
-Here, a uniform random number was generated by numpy.random() of Python.
-\rfig{fig:ObtainedSurfaceNDS}shows the obtained shape and input data for Case (1), where the solid line represents the given wire line.
+We prepared three examples of the simulation.
+Case (1) is a point cloud on a set of a developable surface by a uniform random number using \req{eq:Sur_eq}.
+Case (2) is a point cloud on a sphere whose radius is set on R by a uniform random number.
+\chcolor{Case (3) is a point cloud on a measured shape of a torso, which is a representative breast shape.}
+The simulations aim to confirm that the propose method recreates a given shape and to verify whether a two-piece brassiere cup can be designed to approximate an undevelopable surface that manifests the function of “fitting to a breast”.
+
+\rfig{fig:ObtainedSurfaceNDS} shows the obtained shape and input data for Case (1), where the solid line represents the given wire line.
 Each dotted line denotes the calculated generatrices of the cup shape, and each dot represents a data point.
-\rfig{fig:ObtainedSurfaceDS}shows the obtained pattern where the solid and dotted lines denote the lower and upper edges, respectively.
-Our proposed method produces a cup shape that manifests the function of “fitting to a breast”.
+\rfig{fig:ObtainedSurfaceNDS_Pat} shows the obtained pattern where the solid and dotted lines denote the lower and upper edges, respectively.
+Next, a uniform random number was generated by numpy.random() of Python.
+\rfig{fig:ObtainedSurfaceNDS} shows the obtained shape and input data for Case (2), \chcolor{and \rfig{fig:ObtainedSurfaceNDS2} shows the obtained shape and input data for Case (3) Table \ref{tbl:error and calc} shows the error and calculation time of each case.
+}
 
- \rfig{fig:ObtainedSurfaceDS_Pat}. In \rfig{fig:ObtainedSurfaceDS_Pat}, a solid line and a dotted line represent as same as case(1).
+\chcolor{From the result of case(1), we confirm that our proposed method can recreate a given shape as a two-piece brassire cup.
+And From the result of case(2) and (3), we confirm that our proposed method also can design a two-piece brassiere cup to approximate data points under the conditions.}
 
-\rfig{fig:ObtainedSurfaceNDS_Pat}.
-In \rfig{fig:ObtainedSurfaceNDS_Pat}, each solid line represents a lower edge and a dotted line represents an upper edge.
-In this result, we could confirm that the designed cup shape by our proposed method menifests the function:"fitting to a breast".
-Next, we show the result in case(2). In
-As the calculated shapes approximate the given points, we conclude our proposed method in this paper is useful for efficient design of paper patterns of a two-piece brassiere cup.
+Hence, we conclude our proposed method in this paper is useful for the efficient design of paper patterns of a two-piece brassiere cup.
+\begin{table}[!h]
+	\centering
+	\begin{tabular}{|c|c|c|c|} \hline
+		& Error & Time[sec] \\ \hline
+		case(1) & 0.10 & 1802 \\ \hline
+		case(2) & 0.12 & 740 \\ \hline
+		case(3) & 1.04& 1682 \\ \hline
+	\end{tabular}
+	\caption{The error and calculation time of our proposed method in each case.}
+	\label{tbl:error and calc}
+\end{table}
+
 \begin{figure}[h]
@@
 \section*{CONCLUSION}
-In this paper, we proposed a method to design the cup shape of two-piece brassiere cup and its patterns satisfying the function: "fitting to a breast shape", in case that it is given as a cloud of data points.
-We claimed the background and problem of design process of a brassiere cup.
-In design process, as a cup model for check of the shapes of patterns is made of paper, it is assumed that the surface of the model is composed of several developable surfaces.
-At first, we formulated the cup model based on the differential geometry.
-And we claimed that a developable surface can be determined by two curves included in it.
-The design process of a two-piece brassiere cup can be converted to the optimization problem, whose objective function is the error between the cup shape and its data points.
-In order to calculate the error, we first formulated the error between a point and the surface from geometry condition.
-Then, we proposed a method to divide a data cloud into two clouds: evaluating the lower cup, or evaluating the upper cup.
-In order to verification of our proposed method, we prepared two examples of data points: a set of non-developable surface and developable surface.
-From the result of two examples, we confirmed that our proposed method can design the cup shape which manifests the function.
-As a result, Our proposed method will be useful for efficient design of a two-piece brassiere cup.
-
+\subsection*{Summary}
+Herein we propose a method to design the shape of a two-piece brassiere cup and its patterns to satisfy the function of "fitting to a breast shape" when the shape is given as a cloud of data points.
+In the typical design process, a cup model is made of paper to verify the pattern shape.
+Our model assumes that the model surface is comprised of several developable surfaces.
+First, we formulate the cup model based on differential geometry and hypothesize that a developable surface can be determined by two curves included in it.
+Hence, the design process of a two-piece brassiere cup can be converted into an optimization problem, whose objective function is the error between the cup shape and its data points.
+To calculate the error, first the error between a point and the surface from the geometry condition is formulated.
+Second, our proposed method divides the data cloud into two: the lower and upper cups.
+Then the cups are evaluated.
+To verify our proposed method, we assessed two cases.
+One is a non-developable surface, and the other is a developable surface.
+The results confirm that the proposed method can design a cup shape, which manifests the intended function.
+Consequently, our proposed method should be useful to efficiently design a two-piece brassiere cup.
+\subsection*{Limitation and Future Work}
+\chcolor{Though we proposed a method to design the shape of a two-piece brassiere cup and its patterns to satisfy the function of "fitting to a breast shape" when the shape is given as a cloud of data points, there is still two questions from the point of view of real-world applications.
+One is whether the brassire cup should cover the breast shape.
+A brassire cup has several demands, which include the function to form the ideal breast shape.
+So the function of "fitting to a breast shape" does not only mean fitting to a breast shape itself, but also fitting to an ideal breast shape one wants.
+For future work, it is required to quantify how much fitting to a breast shape and design the brassire cup shape satisfying it.}
 %a this paper, a method to design the cup shape of two-piece brassiere cup and its patterns was proposed when its target shape is given as a cloud of data points.

### 2020-11-25 template/paper/paper_e.tex
CommitFinalBeforeAlign

@@
 \usepackage{bm}
+\usepackage{here}
 %\usepackage[dvipdfmx]{graphicx,xcolor}
@@
 	\subfigure[upper pattern]{
-		\includegraphics[width=0.45\columnwidth]{./figure/UpperPattern.eps}
+		\includegraphics[width=0.45\columnwidth]{./figure/UpperPattern.png}
 		\label{fig:pattern_U}
@@
 	\subfigure[lower pattern]{
-		\includegraphics[width=0.45\columnwidth]{./figure/LowerPattern.eps}
+		\includegraphics[width=0.45\columnwidth]{./figure/LowerPattern.png}
 		\label{fig:pattern_L}
@@
 	\subfigure[lower line]{
-		\includegraphics[width=0.35\columnwidth]{./figure/LowerWire.eps}
+		\includegraphics[width=0.35\columnwidth]{./figure/LowerWire.png}
 		\label{fig:Wire}
@@
 	\centering
-	\includegraphics[scale=0.25]{./figure/Lines.eps}
+	\includegraphics[scale=0.25]{./figure/Lines.png}
 	\caption{Expression of a wire line, a ridge line and an upper line}
@@
 	\centering
-	\includegraphics[width= 1.0 \columnwidth]{./figure/DesignProcess2.eps}
+	\includegraphics[width= 1.0 \columnwidth]{./figure/DesignProcess3.png}
 	\caption{Design process of a brassiere cup}
@@
 But all of them only focus on approximating surface by developable surface, which means that they do not refer to the condition of a developable surface itself.
-When designing a brassiere, it is required to satisfy some conditons of a brassiere cup that designers intend.}
+In designing a brassire cup, it is required not only to fit a breast shape but also to satisfy some conditions.
+For example, the upper line has a point where it is connected with the shoulder strap.
+Hereafter, this point is called the connection point as shown in \rfig{fig:aboutCP}.}
+\begin{figure}[!h]
+		\centering
+		\includegraphics[width = 0.7\columnwidth]{./figure/Connection_Point.png}
+		\caption{Expression about the connection point of a brassiere cup}
+		\label{fig:aboutCP}
+\end{figure}
 
@@
 These lines are obtained by solving the optimization problem when the design parameters are the geodesic curvatures of a pattern shape and the objective function is the error between generatrices determined by the geodesic curvature of a lower edge and the wire line and generatrices determined by the geodesic curvature of an upper edge and the ridge line.
-However, the previously proposed method requires an iterative process to solve the optimization problem for the intended shape\cite{c13}, which is time-consuming.
+However, the previously proposed method requires an iterative process to solve the optimization problem for the intended shape\cite{MyRef,MyRef2}, which is time-consuming.
 Brassiere patterns are typically comprised of two or three pieces.
@@
 	\centering
-	\includegraphics[width = 0.8\columnwidth]{./figure/Object_Coordinates.eps}
+	\includegraphics[width = 0.8\columnwidth]{./figure/Object_Coordinates.png}
 	\caption{Object coordinate system on the surface}
@@
 
-Here, the coefficients of the first fundamental form are represented as
+Based on the theory of surface, the coefficients of the first fundamental form are represented as
 \begin{equation}
@@
 \begin{equation}
-L = \zetavec' \cdot \eta = -\omega_{\xi}, M = \xivec' \cdot \eta = -\omega_{\zeta}.
+L = \zetavec' \cdot \etavec = -\omega_{\xi}, M = \xivec' \cdot \etavec = -\omega_{\zeta}.
 \end{equation}
@@
 
-Note that $s_a$ can take an arbitrary value against $ s_b $. Therefore, the variation of a generatrix $ \Delta \mbold{g} $ is described by total differential form as
+Note that $s_a$ can take an arbitrary value against $ s_b $.
+From \cite{MyRef2}, $ \zetavec_a$ and $\zetavec_b $, which are tangent vectors of $ \mbold{x}_a $ and $ \mbold{x}_b $, and $ \mbold{g} $ satisfy the following equation:
 \begin{equation}
-\Delta \mbold{g} = -\zetavec_a \Delta s_a + \zetavec_b \Delta s_b,
-\end{equation}
-where $ \zetavec_a$ and $\zetavec_b $ are tangent vectors of $ \mbold{x}_a $ and $ \mbold{x}_b $, respectively.
-Next, let $ \Theta $ be the infinitesimal plane surrounded by four vectors $ \zetavec_a \Delta s_a, \zetavec_b \Delta s_b,\mbold{g}$, and $\mbold{g}+\Delta \mbold{g} $ (\rfig{fig:Theta}).
-When the ruled surface is a developable surface, the plane $ \Theta $ is a tangent plane without twisting.
-Therefore, it leads to following equation:
-\begin{equation}
-\det (\zetavec_a, \mbold{g}, \mbold{g}+\Delta \mbold{g})=0
-\label{eq:det_developeq}
-\end{equation}
-Solving \req{eq:det_developeq} gives
-\begin{equation}
-\det (\zetavec_a, \zetavec_b, \mbold{g})=0
+	\det (\zetavec_a, \zetavec_b, \mbold{g})=0. 
 	\label{eq:Cond1}
 \end{equation}
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width = 0.8\columnwidth]{./figure/Theta.eps}
-	\caption{Definition of $ \Theta $}
-	\label{fig:Theta}
-\end{figure}
-\req{eq:Cond1} indicates that the arc length of each curve is subordination.
-When two curves are corresponded to edge lines and $s_b$ can be expressed as $s_b(s_a)$, $\mbold{d}_{\min}\equiv\frac{\mbold{g}}{|\mbold{g}|}$ is established.
+\req{eq:Cond1} indicates that the arc length of each curve is subordination, When two curves are corresponded to edge lines and $ s_b $ can be expressed as $s_b(s_a)$, $ \mbold{d}_{\min}  = \frac{\mbold{g}}{|\mbold{g}|}$ established.
 Then, a rib angle is calculated by \req{eq:d1d2_eq} as follows:
-\begin{equation}
-\alpha = -\sin^{-1}\left( \mbold{d}_{\min} \cdot \zetavec_a \right).
+\begin{equation}\label{eq:alphaEq}
+	\alpha_a = \sin^{-1} \mbold{d}_{\min} \cdot \zeta_a
 \end{equation}
-Using $\mbold{d}_{\min}$ and $\alpha$, $\mbold{\omega}$ can be represented as
+Then, using $ \mbold{d}_{\min} $ and $\alpha $, $ \mbold{\omega} $ can be represented as
 \begin{equation}\label{eq:omegaVec}
-\mbold{\omega} = \left[\begin{array}{c} -\det(\zetavec_a',\zetavec_a, \mbold{d}_{\min} ) \\ \zetavec_a' \cdot \mbold{d}_{\min} \\ \det(\zetavec_a',\zetavec_a, \mbold{d}_{\min} ) \tan \alpha \end{array}\right]
+\mbold{\omega} = \left[\begin{array}{c} -\det(\zetavec_a',\zetavec_a, \mbold{d}_{\min} ) \\ \zetavec_a' \cdot \mbold{d}_{\min} \\ \det(\zetavec_a',\zetavec_a, \mbold{d}_{\min} ) \tan \alpha_a \end{array}\right]
 \end{equation}
@@
 	\subfigure[$ t^*\leq t_{\max} $]{
-		\includegraphics[width=0.45\columnwidth]{./figure/NotExceeding.eps}
+		\includegraphics[width=0.45\columnwidth]{./figure/NotExceeding.png}
 		\label{fig:inD_L}
@@
 	\subfigure[$ t^* > t_{\max} $]{
-		\includegraphics[width=0.45\columnwidth]{./figure/Exceeding.eps}
+		\includegraphics[width=0.45\columnwidth]{./figure/Exceeding.png}
 		\label{fig:inD_U}
@@
 \end{equation}
-Next, consider a “fuzzy” condition for a brassiere cup. The upper line has a point where it is connected with the shoulder strap. Hereafter, this point is called the connection point. 
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width = 0.7\columnwidth]{./figure/Connection_Point.eps}
-	\caption{Expression about the connection point of a brassiere cup}
-	\label{fig:aboutCP}
-\end{figure}
-Typically, this point is given as a fuzzy condition in the design process.
+Next, consider a “fuzzy” condition for a brassiere cup.
+As mentioned, the upper line has a connection point as shown in \rfig{fig:aboutCP}.
+But it is typically given as a fuzzy condition in the design process.
 This can lead to an unexpected error in the optimization problem.
@@
 where $ \mbold{e}_i(s) $ is composed of trigonometric functions with different periods.
-Let $ \mbold{\Phi}_0 = [\xivec_0^\mathrm{T} \;\; \etavec_0^\mathrm{T} \;\; \zetavec_0^\mathrm{T}] $ be the initial basis of the objective coordinate system.
-
+\chcolor{Let $ \mbold{\Phi}_0 = [\xivec_0^\mathrm{T} \;\; \etavec_0^\mathrm{T} \;\; \zetavec_0^\mathrm{T}] $ be the initial basis of the objective coordinate system, $ \mbold{a}_R $ be a set of the vectors $ [\mbold{a}_{\omega_{\xi_R}} \;\; \mbold{a}_{\omega_{\eta_R}} \;\; \mbold{a}_{\upsilon_R}] $ and  $ \mbold{a}_U $ be a set of the vectors $ [\mbold{a}_{\omega_{\xi_U}} \;\; \mbold{a}_{\omega_{\eta_U}} \;\; \mbold{a}_{\upsilon_U}] $.}
 From above, the objective function, which is expressed as \req{eq:ObjectFunc}, and the geometric constraints, which are expressed as  \req{eq:conds_endp1,eq:conds_endp2,eq:conds_DevSur1,eq:conds_DevSur2} are described by the following total parameter vector
@@
 \section*{SIMULATION AND VERIFICATION}
-To demonstrate the utility of our method, we conducted simulations and a verification. For the verification, the infinitesimal rotational ratios vector   of the wire line is given as
+To demonstrate the utility of our method, we conducted simulations and a verification. 
+\subsection*{Simulation Example}
+For simulation, the infinitesimal rotational ratios vector   of the wire line is given as
 \begin{equation}\label{eq:vrf_omgW}
@@
 \end{equation}
-while the connection point $ \mbold{X}_C $ is given as 
+while the connection point $ \mbold{X}_C $ is \chcolor{given in case (1) and (2) as} 
 \begin{equation}\label{eq:givenXc}
@@
 	0 & 0.34 & 0.34
+	\end{array}\right]^\mathrm{T},
+\end{equation}
+We prepared tho examples of the simulation.
+Case (1) is a point cloud on a set of a developable surface by a uniform random number using \req{eq:Sur_eq}.
+Case (2) is a point cloud on a sphere whose radius is set on R by a uniform random number.
+The simulations aim to confirm that the propose method recreates a given shape and to verify whether a two-piece brassiere cup can be designed to approximate an undevelopable surface.
+
+\rfig{fig:ObtainedSurfaceDS} shows the obtained shape and input data for Case (1), where the solid line represents the given wire line.
+Each dotted line denotes the calculated generatrices of the cup shape, and each dot represents a data point.
+\rfig{fig:ObtainedSurfaceDS_Pat} shows the obtained pattern where the solid and dotted lines denote the lower and upper edges, respectively.
+Next, a uniform random number was generated by numpy.random() of Python.
+\rfig{fig:ObtainedSurfaceNDS} shows the obtained shape and input data for Case (2).
+\rtab{tbl:error and calc_Example} shows the error and calculation time of case(1) and (2).
+\begin{table}[h]
+	\centering
+	\begin{tabular}{|c|c|c|} \hline
+		-& Error & Time[sec] \\ \hline
+		case(1) & 0.10 & 1802 \\ \hline
+		case(2) & 0.12 & 740 \\ \hline
+	\end{tabular}
+	\caption{The error and calculation time of our proposed method in case(1) and (2).}
+	\label{tbl:error and calc_Example}
+\end{table}
+For this result, we confirm that our proposed method can recreate a given shape as a two-piece brassire cup and approximate an undevelopable surface.
+
+\subsection*{Experimental Verification}
+For confirming the verification, we measured a breast shape of the torso, which is a typical breast shape, and apply our proposed method to it.
+A wire line is the same as \req{eq:vrf_omgW}, and the connection point is given as
+\begin{equation}\label{eq:givenXc2}
+	\mbold{X}_C = \left[ \begin{array}{ccc}
+	0.2 & 0.41 & 0.27
 	\end{array}\right]^\mathrm{T}.
 \end{equation}
-We prepared three examples of the simulation.
-Case (1) is a point cloud on a set of a developable surface by a uniform random number using \req{eq:Sur_eq}.
-Case (2) is a point cloud on a sphere whose radius is set on R by a uniform random number.
-\chcolor{Case (3) is a point cloud on a measured shape of a torso, which is a representative breast shape.}
-The simulations aim to confirm that the propose method recreates a given shape and to verify whether a two-piece brassiere cup can be designed to approximate an undevelopable surface that manifests the function of “fitting to a breast”.
+In measured the entire shape of a torso, we used the measured point cloud that satisfies $ y \leq 0.2 $ as shown in \rfig{fig:Border}
 
-\rfig{fig:ObtainedSurfaceNDS} shows the obtained shape and input data for Case (1), where the solid line represents the given wire line.
-Each dotted line denotes the calculated generatrices of the cup shape, and each dot represents a data point.
-\rfig{fig:ObtainedSurfaceNDS_Pat} shows the obtained pattern where the solid and dotted lines denote the lower and upper edges, respectively.
-Next, a uniform random number was generated by numpy.random() of Python.
-\rfig{fig:ObtainedSurfaceNDS} shows the obtained shape and input data for Case (2), \chcolor{and \rfig{fig:ObtainedSurfaceNDS2} shows the obtained shape and input data for Case (3) Table \ref{tbl:error and calc} shows the error and calculation time of each case.
-}
-
-\chcolor{From the result of case(1), we confirm that our proposed method can recreate a given shape as a two-piece brassire cup.
-And From the result of case(2) and (3), we confirm that our proposed method also can design a two-piece brassiere cup to approximate data points under the conditions.}
-
-Hence, we conclude our proposed method in this paper is useful for the efficient design of paper patterns of a two-piece brassiere cup.
+\begin{figure}[h]
+	\centering
+	\includegraphics[width = 0.6\columnwidth]{./figure/Measure/SetLine.png}
+	\caption{The border line to use a point cloud in the experiment.}
+	\label{fig:Border}
+\end{figure}  
+\chcolor{The simulations aim to confirm that the propose method whether a two-piece brassiere cup can be designed to approximate an undevelopable surface that manifests the function of “fitting to a breast” .\rfig{fig:ObtainedSurfaceNDS2} shows the obtained shape and input data of experiments,  \rfig{fig:ObtainedSurfaceNDS2_Pat} shows the obtained pattern.
+In \rfig{fig:ObtainedSurfaceNDS2} and \rfig{fig:ObtainedSurfaceNDS2_Pat}, we set $ L_M = 72.8$.
+} \chcolor{\rtab{tbl:error and calc2} shows the error and calculation time of the experiment.
+From the result, we confirm that our proposed method also can design a two-piece brassiere cup to approximate data points under the conditions.
+Hence, we conclude our proposed method in this paper is useful for the efficient design of paper patterns of a two-piece brassiere cup.}
 \begin{table}[!h]
 	\centering
-	\begin{tabular}{|c|c|c|c|} \hline
-		& Error & Time[sec] \\ \hline
-		case(1) & 0.10 & 1802 \\ \hline
-		case(2) & 0.12 & 740 \\ \hline
-		case(3) & 1.04& 1682 \\ \hline
+	\begin{tabular}{|c|c|} \hline
+		Error & Time[sec] \\ \hline
+		1.04& 1682 \\ \hline
 	\end{tabular}
-	\caption{The error and calculation time of our proposed method in each case.}
-	\label{tbl:error and calc}
+	\caption{The error and calculation time of the proposed method in experiment.}
+	\label{tbl:error and calc2}
 \end{table}
@@
 	\subfigure[zx-view]{
-		\includegraphics[width=0.6\columnwidth,clip]{./figure/NDS/ObtainedRidgeLinefromz-x.eps}
-		\label{fig:zx-NDS}
-	}
-	\hfil
-	\subfigure[zy-view]{
-		\includegraphics[width=0.6\columnwidth]{./figure/NDS/ObtainedRidgeLinefromz-y.eps}
-		\label{fig:zy-NDS}
-	}
-	\hfil
-	\subfigure[xy-view]{
-		\includegraphics[width=0.6\columnwidth]{./figure/NDS/ObtainedRidgeLinefromx-y.eps}
-		\label{fig:xy-NDS}
-	}
-	\caption{Obtained shape and input data points in Case(1)}
-	\label{fig:ObtainedSurfaceNDS}
-\end{figure}
-
-\begin{figure}[h!]
-	\centering
-	\subfigure[LOWER PATTERN]{
-		\includegraphics[width=0.6\columnwidth]{./figure/NDS/ObtainedPatternL.eps}
-		\label{fig:low-NDS}
-	}
-	\hfil
-	\subfigure[UPPER PATTERN]{
-		\includegraphics[width=0.6\columnwidth]{./figure/NDS/ObtainedPatternU.eps}
-		\label{fig:upp-NDS}
-	}
-
-	\caption{Obtained patterns in Case(1)}
-	\label{fig:ObtainedSurfaceNDS_Pat}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
-	\subfigure[zx-view]{
-		\includegraphics[width=0.6\columnwidth]{./figure/DS/ObtainedRidgeLinefromz-x.eps}
+		\includegraphics[width=0.6\columnwidth]{./figure/DS/ObtainedRidgeLinefromz-x.png}
 		\label{fig:zx-DS}
@@
 	\subfigure[zy-view]{
-		\includegraphics[width=0.6\columnwidth]{./figure/DS/ObtainedRidgeLinefromz-y.eps}
+		\includegraphics[width=0.6\columnwidth]{./figure/DS/ObtainedRidgeLinefromz-y.png}
 		\label{fig:zy-DS}
@@
 	\subfigure[zy-view]{
-		\includegraphics[width=0.6\columnwidth]{./figure/DS/ObtainedRidgeLinefromx-y.eps}
+		\includegraphics[width=0.6\columnwidth]{./figure/DS/ObtainedRidgeLinefromx-y.png}
 		\label{fig:xy-DS}
@@
 
-\begin{figure}[h!]
+\begin{figure}[h]
 	\centering
-	\subfigure[LOWER PATTERN]{
-		\includegraphics[width=0.6\columnwidth]{./figure/DS/ObtainedPatternL.eps}
+	\subfigure[Lower pattern]{
+		\includegraphics[width=0.6\columnwidth]{./figure/DS/ObtainedPatternL.png}
 		\label{fig:low-DS}
@@
 	\hfil
-	\subfigure[UPPER PATTERN]{
-		\includegraphics[width=0.6\columnwidth]{./figure/DS/ObtainedPatternU.eps}
+	\subfigure[Upper pattern]{
+		\includegraphics[width=0.6\columnwidth]{./figure/DS/ObtainedPatternU.png}
 		\label{fig:upp-DS}
+	}
+	\caption{Obtained patterns in Case(1)}
+	\label{fig:ObtainedSurfaceDS_Pat}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\subfigure[zx-view]{
+		\includegraphics[width=0.6\columnwidth,clip]{./figure/NDS/ObtainedRidgeLinefromz-x.png}
+		\label{fig:zx-NDS}
+	}
+	\hfil
+	\subfigure[zy-view]{
+		\includegraphics[width=0.6\columnwidth]{./figure/NDS/ObtainedRidgeLinefromz-y.png}
+		\label{fig:zy-NDS}
+	}
+	\hfil
+	\subfigure[xy-view]{
+		\includegraphics[width=0.6\columnwidth]{./figure/NDS/ObtainedRidgeLinefromx-y.png}
+		\label{fig:xy-NDS}
+	}
+	\caption{Obtained shape and input data points in Case(2)}
+	\label{fig:ObtainedSurfaceNDS}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\subfigure[Lower pattern]{
+		\includegraphics[width=0.6\columnwidth]{./figure/NDS/ObtainedPatternL.png}
+		\label{fig:low-NDS}
+	}
+	\hfil
+	\subfigure[Upper pattern]{
+		\includegraphics[width=0.6\columnwidth]{./figure/NDS/ObtainedPatternU.png}
+		\label{fig:upp-NDS}
 	}
@@
 	\caption{Obtained patterns in Case(2)}
-	\label{fig:ObtainedSurfaceDS_Pat}
+	\label{fig:ObtainedSurfaceNDS_Pat}
 \end{figure}
+
+\begin{figure}[H]
+	\centering
+	\subfigure[zx-view]{
+		\includegraphics[width=0.6\columnwidth]{./figure/Measure/ObtainedRidgeLinefromz-x.png}
+		\label{fig:zx-NDS2}
+	}
+	\hfil
+	\subfigure[zy-view]{
+		\includegraphics[width=0.6\columnwidth]{./figure/Measure/ObtainedRidgeLinefromz-y.png}
+		\label{fig:zy-NDS2}
+	}
+	\hfil
+	\subfigure[xy-view]{
+		\includegraphics[width=0.6\columnwidth]{./figure/Measure/ObtainedRidgeLinefromx-y.png}
+		\label{fig:xy-NDS2}
+	}
+	\caption{Obtained shape and input data points in the experiment}
+	\label{fig:ObtainedSurfaceNDS2}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\subfigure[Lower pattern]{
+		\includegraphics[width=0.6\columnwidth]{./figure/Measure/ObtainedPatternL.png}
+		\label{fig:low-NDS2}
+	}
+	\hfil
+	\subfigure[Upper pattern]{
+		\includegraphics[width=0.6\columnwidth]{./figure/Measure/ObtainedPatternU.png}
+		\label{fig:upp-NDS2}
+	}
+
+	\caption{Obtained patterns in the experiment}
+	\label{fig:ObtainedSurfaceNDS2_Pat}
+\end{figure}
+
 \section*{CONCLUSION}
@@
 \subsection*{Limitation and Future Work}
-\chcolor{Though we proposed a method to design the shape of a two-piece brassiere cup and its patterns to satisfy the function of "fitting to a breast shape" when the shape is given as a cloud of data points, there is still two questions from the point of view of real-world applications.
-One is whether the brassire cup should cover the breast shape.
+\chcolor{Though we proposed a method to design the shape of a two-piece brassiere cup and its patterns to satisfy the function of "fitting to a breast shape" when the shape is given as a cloud of data points, there is still a  question from the point of view of real-world applications.
+This is whether the brassire cup should cover the breast shape.
 A brassire cup has several demands, which include the function to form the ideal breast shape.
 So the function of "fitting to a breast shape" does not only mean fitting to a breast shape itself, but also fitting to an ideal breast shape one wants.
-For future work, it is required to quantify how much fitting to a breast shape and design the brassire cup shape satisfying it.}
+For future work, to quantify how much fitting a breast shape and controll it are required.}
 %a this paper, a method to design the cup shape of two-piece brassiere cup and its patterns was proposed when its target shape is given as a cloud of data points.
@@
 Wallner, {\it "On Surface Approximation using Developable Surfaces"}, Graphical Models and Image Processing, Volume 61, Issue2, 1999, pp.110-124
+	\bibitem{cX1} Y. Liu, H. Pottmann, J. Wallner, Y.-L. Yang, and W. Wang, {\it "Geometric modeling with conical meshes and developable surfaces"}, Proc.Int. Symp. SIGGRAPH, 2006, pp.681-689
+	\bibitem{cX2} O. Stein, E. Grinspun, and K. Crane, {\it Developability of triangle meshes}, ACM Transaction on Graphics, Vol.37, Issue4, 2018, pp77:1-14
+	\bibitem{cX3} M. Kilian, S. Flöry, Z. Chen, N. J. Mitra, A. Sheffer, and H. Pottmann, {\it Curved folding}, ACM Transaction on Graphics, Vol.27, Issue3, 2008, pp1-9
 	\bibitem{c10} H.Wakamatsu, Y.Ryu, E.Morinaga, E.Arai, and T.
@@
 192-202.
+	\bibitem{MyRef2} Kotaro Yoshida, Hidefumi Wakamatsu, Eiji Morinaga, Seiichiro Tsutsumi, and Takahiro Kubo, {\it Design support of a developable surface considering its bending energy}, Transaction of the JSME, Vol.86, No.890, 2020, pp20-36(in Japanese)
+	\bibitem{cX4} S. Kobayashi, {\it "Differential Geometry of Curves and Surface"}, Shokado, Tokyo, 1995, Chap2 (in Japanse)
 	\bibitem{c13}Elsgolc L.E {\it Calculus of Variations}, Pergamon Press, 1961, pp. 144-157.

### 2021-01-18 template/paper/paper_e.tex
20210119

@@
 
-\author{Kotaro {\sc Yoshida}${}^\dagger$, Hidefumi {\sc Wakamatsu}${}^\dagger$, Eiji {\sc Morinaga}${}^\ddagger$, and Takahiro {\sc Kubo}${}^\S$}
+\author{Kotaro {\sc Yoshida}${}^\dagger$, Hidefumi {\sc Wakamatsu}${}^\dagger$, Eiji {\sc Morinaga}${}^\ddagger$,  Seichiro {\sc Tsutsumi}${}^\S$, Takahiro {\sc Kubo}${}^\P$}
 
@@
 Here, we propose a method to determine a developable surface using two curves that lie on the surface and design a pattern shape.
-Consider the case where the \textit{lower edge} is the curve connecting the lower wire (\rfig{fig:pattern_L}) and the \textit{upper edge} is that combining the upper cup (\rfig{fig:pattern_U}).
+Consider the case where the \textit{lower edge} is the curve connecting the lower wire (\rfig{fig:patterns}(b)) and the \textit{upper edge} is that combining the upper cup (\rfig{fig:patterns}(a)).
 Our method expresses the developable surface using the parameters of a space curve, the condition of two lines that lie on the developable surface, and their obtained pattern shape.
@@
 	\centering
-	\includegraphics[width = \columnwidth]{./figure/PatternImage2.eps}
+	\includegraphics[width = \columnwidth]{./figure/PatternImage2.png}
 	\caption{Description of pattern shape using geodesic curvature of the lower curve}
@@
 \rtab{tbl:error and calc_Example} shows the error and calculation time of case(1) and (2).
-\begin{table}[h]
-	\centering
-	\begin{tabular}{|c|c|c|} \hline
-		-& Error & Time[sec] \\ \hline
-		case(1) & 0.10 & 1802 \\ \hline
-		case(2) & 0.12 & 740 \\ \hline
-	\end{tabular}
-	\caption{The error and calculation time of our proposed method in case(1) and (2).}
-	\label{tbl:error and calc_Example}
-\end{table}
-For this result, we confirm that our proposed method can recreate a given shape as a two-piece brassire cup and approximate an undevelopable surface.
 
-\subsection*{Experimental Verification}
-For confirming the verification, we measured a breast shape of the torso, which is a typical breast shape, and apply our proposed method to it.
-A wire line is the same as \req{eq:vrf_omgW}, and the connection point is given as
-\begin{equation}\label{eq:givenXc2}
-	\mbold{X}_C = \left[ \begin{array}{ccc}
-	0.2 & 0.41 & 0.27
-	\end{array}\right]^\mathrm{T}.
-\end{equation}
-In measured the entire shape of a torso, we used the measured point cloud that satisfies $ y \leq 0.2 $ as shown in \rfig{fig:Border}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width = 0.6\columnwidth]{./figure/Measure/SetLine.png}
-	\caption{The border line to use a point cloud in the experiment.}
-	\label{fig:Border}
-\end{figure}  
-\chcolor{The simulations aim to confirm that the propose method whether a two-piece brassiere cup can be designed to approximate an undevelopable surface that manifests the function of “fitting to a breast” .\rfig{fig:ObtainedSurfaceNDS2} shows the obtained shape and input data of experiments,  \rfig{fig:ObtainedSurfaceNDS2_Pat} shows the obtained pattern.
-In \rfig{fig:ObtainedSurfaceNDS2} and \rfig{fig:ObtainedSurfaceNDS2_Pat}, we set $ L_M = 72.8$.
-} \chcolor{\rtab{tbl:error and calc2} shows the error and calculation time of the experiment.
-From the result, we confirm that our proposed method also can design a two-piece brassiere cup to approximate data points under the conditions.
-Hence, we conclude our proposed method in this paper is useful for the efficient design of paper patterns of a two-piece brassiere cup.}
-\begin{table}[!h]
-	\centering
-	\begin{tabular}{|c|c|} \hline
-		Error & Time[sec] \\ \hline
-		1.04& 1682 \\ \hline
-	\end{tabular}
-	\caption{The error and calculation time of the proposed method in experiment.}
-	\label{tbl:error and calc2}
-\end{table}
-
-\begin{figure}[h]
+\begin{figure}[!h]
 	\centering
@@
 
-\begin{figure}[h]
+\begin{figure}[!h]
 	\centering
 	\subfigure[Lower pattern]{
-		\includegraphics[width=0.6\columnwidth]{./figure/DS/ObtainedPatternL.png}
+		\includegraphics[width=0.8\columnwidth]{./figure/DS/ObtainedPatternL.png}
 		\label{fig:low-DS}
@@
 	\subfigure[Upper pattern]{
-		\includegraphics[width=0.6\columnwidth]{./figure/DS/ObtainedPatternU.png}
+		\includegraphics[width=0.8\columnwidth]{./figure/DS/ObtainedPatternU.png}
 		\label{fig:upp-DS}
@@
 
-\begin{figure}[h]
+\begin{figure}[!h]
 	\centering
@@
 
-\begin{figure}[h]
+\begin{figure}[!h]
 	\centering
 	\subfigure[Lower pattern]{
-		\includegraphics[width=0.6\columnwidth]{./figure/NDS/ObtainedPatternL.png}
+		\includegraphics[width=0.8\columnwidth]{./figure/NDS/ObtainedPatternL.png}
 		\label{fig:low-NDS}
@@
 	\subfigure[Upper pattern]{
-		\includegraphics[width=0.6\columnwidth]{./figure/NDS/ObtainedPatternU.png}
+		\includegraphics[width=0.8\columnwidth]{./figure/NDS/ObtainedPatternU.png}
 		\label{fig:upp-NDS}
@@
 
-\begin{figure}[H]
+\begin{table}[h]
+	\centering
+	\caption{The error and calculation time of our proposed method in case(1) and (2).}
+	\label{tbl:error and calc_Example}
+	\begin{tabular}{|c|c|c|} \hline
+		-& Error & Time[sec] \\ \hline
+		case(1) & 0.10 & 1802 \\ \hline
+		case(2) & 0.12 & 740 \\ \hline
+	\end{tabular}
+\end{table}
+For this result, we confirm that our proposed method can recreate a given shape as a two-piece brassire cup and approximate an undevelopable surface.
+
+\subsection*{Experimental Verification}
+For confirming the verification, we measured a breast shape of the torso, which is a typical breast shape, and apply our proposed method to it.
+A wire line is the same as \req{eq:vrf_omgW}, and the connection point is given as
+\begin{equation}\label{eq:givenXc2}
+	\mbold{X}_C = \left[ \begin{array}{ccc}
+	0.2 & 0.41 & 0.27
+	\end{array}\right]^\mathrm{T}.
+\end{equation}
+\chcolor{In measured the entire shape of a torso, we assumed the measured point cloud covered by a brassiere cup that satisfies $ y \leq 0.2 $ as shown in \rfig{fig:Border}}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width = 0.6\columnwidth]{./figure/Measure/SetLine.png}
+	\caption{The border line to use a point cloud in the experiment,}
+	\label{fig:Border}
+\end{figure}
+\chcolor{where we set $ L_M = 72.8$ in order to convert milimeter into centimenter and set the wire line as  \req{eq:vrf_omgW}.
+The simulations aim to confirm that the propose method whether a two-piece brassiere cup can be designed to approximate an undevelopable surface that manifests the function of “fitting to a breast” .\rfig{fig:ObtainedSurfaceNDS2} shows the obtained shape and input data of experiments,  \rfig{fig:ObtainedSurfaceNDS2_Pat} shows the obtained pattern.} \chcolor{\rtab{tbl:error and calc2} shows the error and calculation time of the experiment.
+From the result, we confirm that our proposed method also can design a two-piece brassiere cup to approximate data points under the conditions.
+Hence, we conclude our proposed method in this paper is useful for the efficient design of paper patterns of a two-piece brassiere cup.}
+
+\begin{figure}[!h]
 	\centering
@@
 
-\begin{figure}[h]
+\begin{figure}[!h]
 	\centering
 	\subfigure[Lower pattern]{
-		\includegraphics[width=0.6\columnwidth]{./figure/Measure/ObtainedPatternL.png}
+		\includegraphics[width=0.8\columnwidth]{./figure/Measure/ObtainedPatternL.png}
 		\label{fig:low-NDS2}
@@
 	\subfigure[Upper pattern]{
-		\includegraphics[width=0.6\columnwidth]{./figure/Measure/ObtainedPatternU.png}
+		\includegraphics[width=0.8\columnwidth]{./figure/Measure/ObtainedPatternU.png}
 		\label{fig:upp-NDS2}
@@
 \end{figure}
+
+\begin{table}[!h]
+	\centering
+	\caption{The error and calculation time of the proposed method in experiment.}
+	\label{tbl:error and calc2}
+	\begin{tabular}{|c|c|} \hline
+		Error & Time[sec] \\ \hline
+		1.04& 1682 \\ \hline
+	\end{tabular}
+\end{table}
 
@@
 \authorbiography{Kotaro, YOSHIDA}{}{Non-Member}{%
-	Kotaro Yoshida received his B.Eng. and M.Eng. degree from Osaka University in 2017 and 2019, respectively. He is doing a doctoral degree at Osaka University.
+	Kotaro Yoshida received his B.Eng. and M.Eng. degree from Osaka University in 2017 and 2019, respectively. He is currently pursuing a doctoral degree at Osaka University.
 }
@@
 	he worked as a Research Associate, Osaka
-	University. He then became an Associate
+	University. In 2007, he was appointed as 
 	Professor at Division of Materials and Manufacturing
@@
 	Researcher at Center for Advanced Science
-	and Innovation, Osaka University. He then became
+	and Innovation, Osaka University. In 2007, he appointed as 
 	an Assistant Professor at Division of Materials and Manufacturing
@@
 
+\authorbiography{Seiichiro, ,TSUTSUMI}{}{Non-Member}{%
+	Seiichiro Tsutsumi received his B.Eng., M.Eng., Ph.D.(Agr.) and  
+	Ph.D.(Eng.) degrees from Kyushu University, Japan, in 1997, 1999, 2002  
+	and 2007, respectively. He worked as a Assistant Professor at Tohoku  
+	University and Kyushu University from 2002 and 2004, respectively. He  
+	then joined at Joining and Welding Research Institute, Osaka University  
+	from 2011 as an Associate Professor. His research interests include  
+	plasticity and fracture of solids. He is a member of JWS, JSCE, JSME,  
+	JASNAOE, etc.
+}
+
 \authorbiography{Takahiro, ,KUBO}{}{Non-Member}{%
@@
 degree in Arts and Sciences from Tokyo University, Japan, in 2010.
-He then joined Wacoal Corp.
-His position is in Human Science Research Center.
+In 2010, he joined Wacoal Corp and works at the Human Science Research Center.
 }
